---
title: "Untitled"
author: "Ruth Kristianingsih"
date: "04/12/2019"
knit: (function(inputFile, encoding) { rmarkdown::render(inputFile, encoding = encoding, output_dir = here::here("reports", stringr::str_remove(getwd(), here::here("scripts/r-scripts/")))) })
output:
  md_document:
    variant: markdown_github
---

# Short analysis of the sequences based on the class

## Introduction

In this report, I am trying to get the information of the sequence of each dataset based on the class, since the heatmap results behave strangely (especially for fungi)

## Execution

```{r}
library(tidyverse)
library(stringr)
library(ggplot2)
```

```{r}
fungi_train <- data.table::fread("../../../../data/getting-data-new/multi-class-data/data-sets/fungi/train.csv")
fungi_val <- data.table::fread("../../../../data/getting-data-new/multi-class-data/data-sets/fungi/val.csv")
fungi_test <- data.table::fread("../../../../data/getting-data-new/multi-class-data/data-sets/fungi/test.csv")

all_fungi <- fungi_train %>% 
  rbind(., fungi_val, fungi_test)
```


```{r}
# Count the length of the string
fungi_seq_info <- all_fungi %>% 
  rowwise() %>% 
  dplyr::mutate(len = stringr::str_length(sequence))
```

```{r}
fungi_seq_info %>% 
  summary(len)
```

```{r}
ggplot(fungi_seq_info) +
  aes(len) +
  geom_histogram()
```


## Getting fasta data

Since we know that all of effectors data are secreted, then we do not need to use SignalP to identify wether it is secreted or not. Now we just need to deal with the non-effector data.

### Change the dataframe in R to the fasta data

```{r}
# Load all of the fungi data
fungi_train <- data.table::fread("../../../../data/getting-data-new/multi-class-data/data-sets/fungi/train.csv")
fungi_val <- data.table::fread("../../../../data/getting-data-new/multi-class-data/data-sets/fungi/val.csv")
fungi_test <- data.table::fread("../../../../data/getting-data-new/multi-class-data/data-sets/fungi/test.csv")

# Load all of the bacteria data
bacteria_train <- data.table::fread("../../../../data/getting-data-new/multi-class-data/data-sets/bacteria/train.csv")
bacteria_val <- data.table::fread("../../../../data/getting-data-new/multi-class-data/data-sets/bacteria/val.csv")
bacteria_test <- data.table::fread("../../../../data/getting-data-new/multi-class-data/data-sets/bacteria/test.csv")

# Load all of the oomycete data
oomycete_train <- data.table::fread("../../../../data/getting-data-new/multi-class-data/data-sets/oomycete/train.csv")
oomycete_val <- data.table::fread("../../../../data/getting-data-new/multi-class-data/data-sets/oomycete/val.csv")
oomycete_test <- data.table::fread("../../../../data/getting-data-new/multi-class-data/data-sets/oomycete/test.csv")
```

```{r}
get_non_eff <- function(data){
  non_eff <- data %>% 
    dplyr::filter(label == 0) %>% 
    dplyr::select(sequence) %>% 
    tibble::rowid_to_column() %>% 
    `colnames<-` (c("seq_name", "sequence"))
  
  return(non_eff)
}
```

```{r}
fungi_train_non_eff <- get_non_eff(fungi_train)
fungi_val_non_eff <- get_non_eff(fungi_val)
fungi_test_non_eff <- get_non_eff(fungi_test)

bacteria_train_non_eff <- get_non_eff(bacteria_train)
bacteria_val_non_eff <- get_non_eff(bacteria_val)
bacteria_test_non_eff <- get_non_eff(bacteria_test)

oomycete_train_non_eff <- get_non_eff(oomycete_train)
oomycete_val_non_eff <- get_non_eff(oomycete_val)
oomycete_test_non_eff <- get_non_eff(oomycete_test)
```

### Change the dataframe to fasta

```{r}
library("seqRFLP")
```

```{r}
# Define a function to get teh fasta from the df using package "seqRFLP"
get_fasta <- function(data){
  dat = dataframe2fas(get(data), file = paste0(data, ".fasta"))
}
```


```{r}
get_fasta("fungi_val_non_eff")
```

```{r}
list_data_name <- c("fungi_train_non_eff", 
                    "fungi_val_non_eff", 
                    "fungi_test_non_eff", 
                    "bacteria_train_non_eff", 
                    "bacteria_val_non_eff", 
                    "bacteria_test_non_eff", 
                    "oomycete_train_non_eff", 
                    "oomycete_val_non_eff", 
                    "oomycete_test_non_eff")
```

```{r}
# Using for loop to make it easier to automatically run the function at once
for (data in list_data_name){
  get_fasta(data)
}
```




