---
title: "Untitled"
author: "Ruth Kristianingsih"
date: "02/04/2020"
knit: (function(inputFile, encoding) { rmarkdown::render(inputFile, encoding = encoding, output_dir = here::here("reports", stringr::str_remove(getwd(), here::here("scripts/r-scripts/")))) })
output:
  md_document:
    variant: markdown_github
---

# Evaluate the existed data on the EffectorP 

## Introduction

Since all of the ensemble results have been done, checking the perfomance of the existed tools on the data we have is necessary as a tool/parameter to compare how good or bad the perfomance of the model we built. 

## Method

In this report, I will show the prediction results of both effectorP 1.0 and 2.0 on each dataset I have. 

## Hypothesis

Since effectorP is a tool to predict effector protein, then this model may perform better on fungi datasets than bacteria and oomycete datasets. 

## Functions 

```{r setup, include = FALSE}
# Load library
library(dplyr)
library(stringr)
library(caret)
```

```{r}
get_data_ready <- function(data){
  
  data <- data %>% 
  dplyr::select(-c("Probability")) %>% 
  `colnames<-`(c("identifier", "prediction")) %>% 
  dplyr::mutate(prediction = case_when(
    prediction == "Effector" ~ 1, 
    TRUE ~ 0
  )) %>% 
  dplyr::mutate(label = stringr::str_remove_all(identifier, ".*_"), 
                identifier =  stringr::str_extract(identifier, "[^_]*"))
  
  return(data)
}
```


```{r}
calculate_accuracy <- function(data) {
  
  data <- get_data_ready(data)
  
  # Calculate tab
  tab <- table(data %>% 
                 dplyr::select(prediction) %>% 
                 pull(), 
               data %>% 
                 dplyr::select(label) %>% 
                 pull())

  # Calculate acc
  acc <- confusionMatrix(tab)$overall["Accuracy"]
  
  return(acc)
}
```


```{r}
get_confusion_matrix_df <- function(data){
  
  df_name <- deparse(substitute(data))
  df_name_split <- df_name %>% stringr::str_split("_") %>% unlist() 
  
  data_ready <- get_data_ready(data)

  # Calculate confusion matrix
  tab <- table(data_ready %>% 
                 dplyr::select(prediction) %>% 
                 pull(), 
               data_ready %>% 
                 dplyr::select(label) %>% 
                 pull()) %>% 
    as.data.frame() %>% 
    `colnames<-`(c("prediction", "label", "freq")) %>% 
    dplyr::mutate(dataset = paste0(df_name_split[1], "_", df_name_split[2]),
                  effectorP_version = df_name_split[4])
  
  return(tab)
}
```

## Results

### Bacteria

```{r}
# Load prediction results from EffectorP 1.0
bacteria_train_effectorp_1 <- data.table::fread("../../../data/secreted_data/pred_effectorP/effectorP_1/pred_effectorp_1_bacteria_training.csv")
bacteria_val_effectorp_1 <- data.table::fread("../../../data/secreted_data/pred_effectorP/effectorP_1/pred_effectorp_1_bacteria_validation.csv")
bacteria_test_effectorp_1 <- data.table::fread("../../../data/secreted_data/pred_effectorP/effectorP_1/pred_effectorp_1_bacteria_testing.csv")

# Load prediction results from EffectorP 2.0
bacteria_train_effectorp_2 <- data.table::fread("../../../data/secreted_data/pred_effectorP/effectorP_2/pred_effectorp_2_bacteria_training.csv")
bacteria_val_effectorp_2 <- data.table::fread("../../../data/secreted_data/pred_effectorP/effectorP_2/pred_effectorp_2_bacteria_validation.csv")
bacteria_test_effectorp_2 <- data.table::fread("../../../data/secreted_data/pred_effectorP/effectorP_2/pred_effectorp_2_bacteria_testing.csv")
```

```{r}
bacteria_on_effectorP <- data.frame(data = c("bacteria_train", 
                                               "bacteria_val", 
                                               "bacteria_test"), 
                                      acc_effectorP_1 = c(calculate_accuracy(bacteria_train_effectorp_1), 
                                                         calculate_accuracy(bacteria_val_effectorp_1), 
                                                         calculate_accuracy(bacteria_test_effectorp_1)), 
                                      acc_effectorP_2 = c(calculate_accuracy(bacteria_train_effectorp_2), 
                                                         calculate_accuracy(bacteria_val_effectorp_2), 
                                                         calculate_accuracy(bacteria_test_effectorp_2)))
bacteria_on_effectorP 
```



### Fungi

```{r}
# Load prediction results from EffectorP 1.0
fungi_train_effectorp_1 <- data.table::fread("../../../data/secreted_data/pred_effectorP/effectorP_1/pred_effectorp_1_fungi_training.csv")
fungi_val_effectorp_1 <- data.table::fread("../../../data/secreted_data/pred_effectorP/effectorP_1/pred_effectorp_1_fungi_validation.csv")
fungi_test_effectorp_1 <- data.table::fread("../../../data/secreted_data/pred_effectorP/effectorP_1/pred_effectorp_1_fungi_testing.csv")


# Load prediction results from EffectorP 2.0
fungi_train_effectorp_2 <- data.table::fread("../../../data/secreted_data/pred_effectorP/effectorP_2/pred_effectorp_2_fungi_training.csv")
fungi_val_effectorp_2 <- data.table::fread("../../../data/secreted_data/pred_effectorP/effectorP_2/pred_effectorp_2_fungi_validation.csv")
fungi_test_effectorp_2 <- data.table::fread("../../../data/secreted_data/pred_effectorP/effectorP_2/pred_effectorp_2_fungi_testing.csv")
```

```{r}
fungi_on_effectorP <- data.frame(data = c("fungi_train", 
                                            "fungi_val", 
                                            "fungi_test"), 
                                  acc_effectorP_1 = c(calculate_accuracy(fungi_train_effectorp_1), 
                                                    calculate_accuracy(fungi_val_effectorp_1), 
                                                    calculate_accuracy(fungi_test_effectorp_1)),
                                   acc_effectorP_2 = c(calculate_accuracy(fungi_train_effectorp_2), 
                                                    calculate_accuracy(fungi_val_effectorp_2), 
                                                    calculate_accuracy(fungi_test_effectorp_2)))

fungi_on_effectorP
```

### Oomycete

```{r}
# Load prediction results from EffectorP 1.0
oomycete_train_effectorp_1 <- data.table::fread("../../../data/secreted_data/pred_effectorP/effectorP_1/pred_effectorp_1_oomycete_training.csv")
oomycete_val_effectorp_1 <- data.table::fread("../../../data/secreted_data/pred_effectorP/effectorP_1/pred_effectorp_1_oomycete_validation.csv")
oomycete_test_effectorp_1 <- data.table::fread("../../../data/secreted_data/pred_effectorP/effectorP_1/pred_effectorp_1_oomycete_testing.csv")

# Load prediction results from EffectorP 2.0
oomycete_train_effectorp_2 <- data.table::fread("../../../data/secreted_data/pred_effectorP/effectorP_2/pred_effectorp_2_oomycete_training.csv")
oomycete_val_effectorp_2 <- data.table::fread("../../../data/secreted_data/pred_effectorP/effectorP_2/pred_effectorp_2_oomycete_validation.csv")
oomycete_test_effectorp_2 <- data.table::fread("../../../data/secreted_data/pred_effectorP/effectorP_2/pred_effectorp_2_oomycete_testing.csv")
```

```{r}
oomycete_on_effectorP <- data.frame(data = c("oomycete_train", 
                                            "oomycete_val", 
                                            "oomycete_test"), 
                                  acc_effectorP_1 = c(calculate_accuracy(oomycete_train_effectorp_1), 
                                                    calculate_accuracy(oomycete_val_effectorp_1), 
                                                    calculate_accuracy(oomycete_test_effectorp_1)), 
                                   acc_effectorP_2 = c(calculate_accuracy(oomycete_train_effectorp_2), 
                                                    calculate_accuracy(oomycete_val_effectorp_2), 
                                                    calculate_accuracy(oomycete_test_effectorp_2)))

oomycete_on_effectorP
```

All data together:

```{r}
rbind(bacteria_on_effectorP, 
      oomycete_on_effectorP, 
      fungi_on_effectorP) %>% 
  knitr::kable()
```

### Further on fungi data

```{r}
fungi_pred_both_effectorP <- rbind(get_confusion_matrix_df(fungi_train_effectorp_1), 
      get_confusion_matrix_df(fungi_val_effectorp_1), 
      get_confusion_matrix_df(fungi_test_effectorp_1), 
      get_confusion_matrix_df(fungi_train_effectorp_2), 
      get_confusion_matrix_df(fungi_val_effectorp_2), 
      get_confusion_matrix_df(fungi_test_effectorp_2))

fungi_pred_both_effectorP
```

```{r}
# Make the datasets in order
neworder <- c("fungi_train","fungi_val","fungi_test")

fungi_pred_both_effectorP <- fungi_pred_both_effectorP %>% 
  dplyr::mutate(dataset = factor(dataset, levels = neworder))

fungi_pred_both_effectorP  %>% 
  ggplot() +
  aes(x = label, y = prediction) +
  geom_tile(aes(fill = freq), colour = "white") +
  geom_text(aes(label = freq), vjust = 0.5) +
  scale_fill_viridis_c(begin = 0.1, end = 1) +
  labs(x = "True value", y = "Prediction") +
  facet_grid(effectorP_version ~ dataset) +
  coord_fixed() +
  theme_light()
```

## Conclusion

Since both version 1.0 and 2.0 are trained on fungi datasets, therefore, it performs better on fungi dataset than other datasets. 





