---
title: "Untitled"
author: "Ruth Kristianingsih"
date: "03/04/2020"
knit: (function(inputFile, encoding) { rmarkdown::render(inputFile, encoding = encoding, output_dir = here::here("reports", stringr::str_remove(getwd(), here::here("scripts/r-scripts/")))) })
output:
  md_document:
    variant: markdown_github
---

# Evaluate our data on the existed tool DeepT3

## Introduction

In this report, a results of a prediction from DeepT3 will be shown and the accuracy results will be calculated. Note that the cut-off / threshold of this model is 0.5. 

## Results

### Define functions


```{r setup, include = FALSE}
# Load libraries
library(seqinr)
library(dplyr)
library(stringr)
library(caret)
```

```{r}
fasta_to_df <- function(file_path) {
  file_path %>%
    seqinr::read.fasta() %>%
    purrr::map(
      .f = function(x) {
        data.frame(
          c(
            x %>% attributes() %>% unlist(),
            x %>%
              paste0(collapse = "") %>%
              stringr::str_to_upper() %>%
              `names<-`("sequence")
          ) %>% 
          rbind()
        )
      }
    ) %>% 
    purrr::reduce(rbind) %>% 
    tibble::remove_rownames()
}
```

```{r}
get_data_ori_ready <- function(path){
  
  data <- path %>% 
    fasta_to_df() %>%
    dplyr::select(name) %>% 
    `colnames<-`(c("id")) %>% 
    dplyr::mutate(label = stringr::str_remove_all(id, ".*_"), 
                  id =  stringr::str_extract(id, "[^_]*"))
  
  return(data)
}
```

```{r}
get_prediction <- function(path){
  
  data <- data.table::fread(path, header = FALSE) %>% 
  `colnames<-`(c("pred")) %>% 
  dplyr::mutate(pred = case_when(
  pred == "T3SE" ~ 1, 
  TRUE ~ 0
  ))
  
  return(data)
}
```

```{r}
calculate_accuracy <- function(true_data, pred_data) {
  
  tab <- table(pred_data %>% 
                 dplyr::select(pred) %>% 
                 pull(), 
               true_data %>% 
                 dplyr::select(label) %>% 
                 pull())

  # Calculate acc
  acc <- confusionMatrix(tab)$overall["Accuracy"]
  
  return(acc)
}
```

### Evaluate model on bacteria data

Get the original data: 

```{r}
bacteria_train_original_data <- get_data_ori_ready("../../../data/secreted_data/ready_to_process/fasta_files/bacteria_training.fasta")
   
bacteria_val_original_data <- get_data_ori_ready("../../../data/secreted_data/ready_to_process/fasta_files/bacteria_validation.fasta") 

bacteria_test_original_data <- get_data_ori_ready("../../../data/secreted_data/ready_to_process/fasta_files/bacteria_testing.fasta")
```

Get the prediction results:

```{r}
pred_bacteria_train <- get_prediction("../../../data/secreted_data/pred_deept3/result_training.txt")
pred_bacteria_val <- get_prediction("../../../data/secreted_data/pred_deept3/result_validation.txt")
pred_bacteria_test <- get_prediction("../../../data/secreted_data/pred_deept3/result_testing.txt")
```

```{r}
data.frame(data = c("bacteria_train", 
                    "bacteria_val", 
                    "bacteria_test"), 
           acc_deepT3 = c(calculate_accuracy(bacteria_train_original_data, pred_bacteria_train),
                          calculate_accuracy(bacteria_val_original_data, pred_bacteria_val),
                          calculate_accuracy(bacteria_test_original_data, pred_bacteria_test))) %>% 
  knitr::kable()
```

### Evaluate model on oomycete and fungi-data

Get the original data or the true label:

```{r}
oomycete_testing_original_data <- get_data_ori_ready("../../../data/secreted_data/ready_to_process/fasta_files/oomycete_testing.fasta") 
fungi_testing_original_data <- get_data_ori_ready("../../../data/secreted_data/ready_to_process/fasta_files/fungi_testing.fasta")
```


Get the prediction results for both oomycete and fungi:

```{r}
pred_oomycete_test <- get_prediction("../../../data/secreted_data/pred_deept3/result_oomycete_testing.txt")
pred_fungi_test <- get_prediction("../../../data/secreted_data/pred_deept3/result_fungi_testing.txt")
```

Accuracy:

```{r}
data.frame(data = c("fungi_test", 
                    "oomycete_test"), 
           acc_deepT3 = c(calculate_accuracy(fungi_testing_original_data, pred_fungi_test),
                          calculate_accuracy(oomycete_testing_original_data, pred_oomycete_test))) %>% 
  knitr::kable()
```

### Conclusion

The results apart from bacteria datasets are still very poor, this is because the model is trained on the bacteria data only. 
