---
title: "Untitled"
author: "Ruth Kristianingsih"
date: "04/02/2020"
knit: (function(inputFile, encoding) { rmarkdown::render(inputFile, encoding = encoding, output_dir = here::here("reports", stringr::str_remove(getwd(), here::here("scripts/r-scripts/")))) })
output:
  md_document:
    variant: markdown_github
---

# Results of Hyperscan of the Effector and Non-effector (All secreted data) on different architecture

## Background

In this report, all differenct results in hyperparameter scan for several different models for different datasets will be shown.  

```{r}
# Load libabry needed
library(tidyverse)
```

## Oomycete

### CNN-GRU

The memory used in cluster:

```
Job ID: 25614469
Cluster: ciscluster
User/Group: kristian/TSL_2t
State: COMPLETED (exit code 0)
Cores: 1
CPU Utilized: 13:18:32
CPU Efficiency: 99.91% of 13:19:17 core-walltime
Job Wall-clock time: 13:19:17
Memory Utilized: 8.71 GB
Memory Efficiency: 21.79% of 40.00 GB
```

```{r}
oomycete_cnn_gru_secreted <- data.table::fread("../../../../../data/secreted_data/training-results/oomycete/results/secreted_hyper_scan/df_pred_results_cnn_gru_scan_oomycete_secreted.csv")

oomycete_cnn_gru_all_scan_result <- data.table::fread("../../../../../data/secreted_data/training-results/oomycete/results/secreted_hyper_scan/all_scan_results_cnn_gru_scan_oomycete_secreted.csv") %>% 
  dplyr::select(c(params, mean_test_score))

oomycete_cnn_gru_secreted %>% 
  arrange(desc(Accuracy)) %>% 
  knitr::kable()


oomycete_cnn_gru_all_scan_result %>% 
  arrange(desc(mean_test_score)) %>% 
  knitr::kable()
```

### GRU-Embedding

```{r}
oomycete_gru_emb_results_all <- data.table::fread("../../../../../data/secreted_data/training-results/oomycete/results/secreted_hyper_scan/oomycete_scan_results_gru_embedding_scan_oomycete.csv") %>% 
  dplyr::select(c(params, mean_test_score))


oomycete_gru_emb_results <- data.table::fread("../../../../../data/secreted_data/training-results/oomycete/results/secreted_hyper_scan/df_pred_results_gru_embedding_scan_oomycete.csv")
```


```{r}
oomycete_gru_emb_results %>% 
  arrange(desc(Accuracy)) %>% 
  knitr::kable()
```

### LSTM-Embedding

```{r}
oomycete_lstm_embd_all_results <- data.table::fread("../../../../../data/secreted_data/training-results/oomycete/results/secreted_hyper_scan/all_scan_results_lstm_emb_scan_oomycete.csv") %>% 
  dplyr::select(c(params, mean_test_score))

oomycete_lstm_embd_all_results %>% 
  arrange(desc(mean_test_score)) %>% 
  knitr::kable()
```

### CNN-LSTM

```{r}
oomycete_cnn_lstm_pred <- data.table::fread("../../../../../data/secreted_data/training-results/oomycete/results/secreted_hyper_scan/df_pred_results_cnn_lstm_scan_oomycete_secreted_data.csv")
oomycete_cnn_lstm_all <- data.table::fread("../../../../../data/secreted_data/training-results/oomycete/results/secreted_hyper_scan/all_scan_results_cnn_lstm_scan_oomycete_secreted_data.csv")

oomycete_cnn_lstm_pred %>% 
  arrange(desc(Accuracy)) %>% 
  knitr::kable()
```


## Fungi

### CNN-GRU

```{r}
fungi_cnn_gru_secreted <- data.table::fread("../../../../../data/secreted_data/training-results/fungi/df_pred_results_cnn_gru_fungi_secreted.csv")

fungi_cnn_gru_secreted %>% 
  arrange(desc(Accuracy)) %>% 
  knitr::kable()
```

### LSTM Emb

```{r}
fungi_lstm_emb_all <- data.table::fread("../../../../../data/secreted_data/training-results/fungi/all_scan_results_lstm_emb_scan_fungi.csv") %>% 
   dplyr::select(c(params, mean_test_score))
 

fungi_lstm_emb_all %>% 
  dplyr::arrange(desc(mean_test_score)) %>% 
  head(10) %>% 
  knitr::kable()
```



## Bacteria

## CNN-GRU

```{r}
bacteria_cnn_gru_secreted <- data.table::fread("../../../../../data/secreted_data/training-results/bacteria/df_pred_results_cnn_gru_bacteria_secreted.csv") 


bacteria_cnn_gru_pred_all <- data.table::fread("../../../../../data/secreted_data/training-results/bacteria/all_scan_results_cnn_gru_bacteria_secreted.csv") %>% 
  dplyr::select(c(params, mean_test_score))


bacteria_cnn_gru_secreted %>% 
  dplyr::arrange(desc(Accuracy)) %>% 
  knitr::kable()


bacteria_cnn_gru_pred_all %>% 
  dplyr::arrange(desc(mean_test_score)) %>% 
  knitr::kable()
```

## CNN-LSTM

```{r}
bacteria_cnn_lstm_secreted <- data.table::fread("../../../../../data/secreted_data/training-results/bacteria/df_pred_results_cnn_lstm_scan_bacteria_secreted.csv") 


bacteria_cnn_lstm_pred_all <- data.table::fread("../../../../../data/secreted_data/training-results/bacteria/all_scan_results_cnn_lstm_scan_bacteria_secreted.csv") %>% 
  dplyr::select(c(params, mean_test_score))


bacteria_cnn_lstm_secreted %>% 
  dplyr::arrange(desc(Accuracy)) %>% 
  knitr::kable()


bacteria_cnn_lstm_pred_all %>% 
  dplyr::arrange(desc(mean_test_score)) %>% 
  knitr::kable()
```

## GRU-EMb

```{r}
bacteria_gru_emb_pred <- data.table::fread("../../../../../data/secreted_data/training-results/bacteria/df_pred_results_gru_embedding_scan_all.csv") 


bacteria_gru_emb_all <- data.table::fread("../../../../../data/secreted_data/training-results/bacteria/bacteria_scan_results_gru_embedding_scan_all.csv") %>% 
  dplyr::select(c(params, mean_test_score))

bacteria_gru_emb_all %>% 
  dplyr::arrange(desc(mean_test_score)) %>% 
  head(10) %>% 
  knitr::kable()

bacteria_gru_emb_pred %>% 
  dplyr::arrange(desc(Accuracy)) %>% 
  knitr::kable()
```

## LSTM-Emb

```{r}
bacteria_latm_emb_scan_all <- data.table::fread("../../../../../data/secreted_data/training-results/bacteria/all_scan_results_lstm_emb_scan_bacteria.csv") %>% 
   dplyr::select(c(params, mean_test_score))
 

bacteria_latm_emb_scan_all %>% 
  dplyr::arrange(desc(mean_test_score)) %>% 
  head(10) %>% 
  knitr::kable()
```



## All data together

```{r}
all_data_cnn_gru_pred_res <- data.table::fread("../../../../../data/secreted_data/training-results/all/df_pred_results_cnn_gru_all.csv")

all_data_cnn_gru_pred_res %>% 
  dplyr::arrange(desc(Accuracy)) %>% 
  knitr::kable()
```

```{r}
all_data_lstm_emb_all <- data.table::fread("../../../../../data/secreted_data/training-results/all/all_scan_results_lstm_emb_scan_all_data.csv") %>% select(params, mean_test_score)

all_data_lstm_emb_all %>% 
  dplyr::arrange(desc(mean_test_score)) %>% 
  knitr::kable()
```




## Summary Comparing results of training data with the effector secreted and non-secreted 

```r
data.frame(model = c("cnn_gru_bacteria", 
                         "cnn_gru_bacteria", 
                         "cnn_gru_fungi", 
                         "cnn_gru_fungi", 
                         "cnn_gru_oomycete", 
                         "cnn_gru_oomycete"), 
           data = c("non-secreted", 
                    "secreted", 
                    "non-secreted", 
                    "secreted", 
                    "non-secreted", 
                    "secreted"),
           accuracy = c(bacteria_cnn_gru %>% dplyr::select(Accuracy) %>% max(), 
                        bacteria_cnn_gru_secreted %>% dplyr::select(Accuracy) %>% max(),
                        fungi_cnn_gru %>% dplyr::select(Accuracy) %>% max(),
                        fungi_cnn_gru_secreted %>% dplyr::select(Accuracy) %>% max(),
                        oomycete_cnn_gru %>% dplyr::select(Accuracy) %>% max(),
                        oomycete_cnn_gru_secreted %>% dplyr::select(Accuracy) %>% max())
)
```






