---
title: ''
author: "Ruth Kristianingsih"
date: "17/02/2020"
knit: (function(inputFile, encoding) { rmarkdown::render(inputFile, encoding = encoding, output_dir = here::here("reports", stringr::str_remove(getwd(), here::here("scripts/r-scripts/")))) })
output:
  md_document:
    variant: markdown_github
---

# Manually tuning model for Fungi 

## Background

In this report, manually tuning models for pathogen fungi will be done. 

```{r setup}
library(tidyverse)
library(patchwork)
library(parscanlogreader)
source("../../../r-functions/plot_training_vs_validation.R")

#import the package
library(randomForest)
```


## Results from hypeparameter scan

```{r}
fungi_cnn_gru_secreted <- data.table::fread("../../../../../data/secreted_data/training-results/fungi/df_pred_results_cnn_gru_fungi_secreted.csv")

fungi_cnn_gru_secreted %>% 
  arrange(desc(Accuracy)) %>% 
  knitr::kable()
```

```{r}
fungi_cnn_gru_secreted  <- fungi_cnn_gru_secreted %>%  
  separate(Parameters, c("reg_rate", "optimizers", "opt_go_backwards", "opt_dropout_recurrent", "opt_dropout", "maxpool_size", "kernel_size", "gru_hidden_units", "filter_conv", "epochs", "batch_size", "activation_conv"), sep = ", ")
```

```{r}
fungi_cnn_gru_secreted <- fungi_cnn_gru_secreted %>% 
  # dplyr::select(-c(V1, Accuracy)) %>%
  mutate_at(
    .vars = dplyr::vars(reg_rate, optimizers, opt_go_backwards, opt_dropout_recurrent, opt_dropout, maxpool_size, kernel_size, gru_hidden_units, filter_conv, epochs, batch_size, activation_conv),
    .funs = function(x) {
      stringr::str_replace_all(
        string = x,
        pattern = "(.+?:)",
        replacement = ""
      )  %>% 
  stringr::str_remove_all("\\'|\\}")
    }
  )
```


```{r}
fungi_cnn_gru_secreted %>% 
  dplyr::select(-c(V1, Accuracy)) 
```


## Short analysis using Randomforest

```{r}
data <- fungi_cnn_gru_secreted %>% 
  dplyr::select(-c("Sensitivity", "Specifity"))

cols <- c("reg_rate", "optimizers", "opt_go_backwards", "opt_dropout_recurrent", "opt_dropout", "maxpool_size", "kernel_size", "gru_hidden_units", "filter_conv", "epochs", "batch_size", "activation_conv")

data[cols] <- lapply(data[cols], factor)

data %>% 
  colnames()

# Perform training:
test <- randomForest(Accuracy ~ .,
                            data = data, 
                            ntree = 100, 
                            mtry = 2, 
                            importance=TRUE)
```

```{r}
mtry_list <- c(2:10)

num_iter <- length(mtry_list)
var_explained <- numeric(length = num_iter)

for (i in 1:num_iter) {
  rf_classifier <- randomForest(
    Accuracy ~ .,
    data = data,
    ntree = 1000,
    mtry = mtry_list[i],
    importance = TRUE
  )
  var_explained[i] <- rf_classifier$rsq[1000] * 100
}


df <- data.frame(mtry_list, var_explained)

df %>% 
  knitr::kable()
```

```{r}
gg <- ggplot(df) +
  aes(x = mtry_list, y = var_explained) +
  geom_point()


gg
```


## Model

```bash
# Define the base model architecture
def simple_CNN_GRU(filter_conv,
			             kernel_size,
			             maxpool_size,
			             activation_conv,
			             gru_hidden_units,
                   opt_dropout,
                   opt_dropout_recurrent,
                   opt_go_backwards,
                   reg_rate,
			             optimizers):
  model = Sequential()
  model.add(Conv1D(filters = filter_conv,
		               kernel_size = kernel_size,
		               strides = 1,
	                 activation = activation_conv,
	                 input_shape =  (4034, 20)))
  model.add(MaxPooling1D(maxpool_size))
  model.add(Bidirectional(GRU(units = gru_hidden_units,
                                activation = 'tanh',
                                recurrent_activation = 'hard_sigmoid',
                                kernel_regularizer = regularizers.l2(reg_rate),
                                recurrent_regularizer = regularizers.l2(reg_rate),
                                dropout = opt_dropout,
                                recurrent_dropout = opt_dropout_recurrent,
                                go_backwards = opt_go_backwards)))
  model.add(Dense(1, activation = 'sigmoid'))
  model.compile(loss = 'binary_crossentropy',
                optimizer = optimizers,
                metrics = ['accuracy'])
  print(model.summary())
  return model
  
  
 model = simple_CNN_GRU(filter_conv = 8,
			                     kernel_size = 1,
			                     maxpool_size = 2,
			                     activation_conv = None,
			                     gru_hidden_units = 8,
                           opt_dropout = 0,
                           opt_dropout_recurrent = 0,
                           opt_go_backwards = 'TRUE',
                           reg_rate = 0.001,
			                     optimizers = 'Adam')

	# Fit the model
    history_fit = model.fit(x_train[train], y_train[train], epochs = 60, batch_size = 8, verbose = 1, shuffle = 1, validation_data = (x_train[test], y_train[test]))
```

## Load library

```{r, include = FALSE}
library(tidyverse)
library(patchwork)
source("../../../r-functions/plot_training_vs_validation.R")
```

### CNN-GRU results

```{r}
# Load data for 30 epochs
fungi_cnn_gru_train_30epochs <- data.table::fread("../../../../../results/secreted_data_run_manually/fungi/df_results_train_cnn_gru_best_fungi.csv")
fungi_cnn_gru_val_30epochs <- data.table::fread("../../../../../results/secreted_data_run_manually/fungi/df_results_val_cnn_gru_best_fungi.csv")
fungi_cnn_gru_test_30epochs <- data.table::fread("../../../../../results/secreted_data_run_manually/fungi/df_results_test_cnn_gru_best_fungi.csv")


# Adding the average on the table 

fungi_cnn_gru_train_30epochs <- fungi_cnn_gru_train_30epochs %>% 
  dplyr::mutate(AVG_CV = rowMeans(.[,2:6]))

fungi_cnn_gru_val_30epochs <- fungi_cnn_gru_val_30epochs %>% 
  dplyr::mutate(AVG_CV =rowMeans(.[,2:6]))
```

```{r}
get_gg_acc(fungi_cnn_gru_train_30epochs, fungi_cnn_gru_val_30epochs,  plot_title = "") +
  facet_wrap(~CV, nrow = 2 )
```

#### Change the epochs -- train the model longer

From the figure above, it seems that the accuracy can increase futher, therefore increasing the number epochs will give us better idea:

```{r}
# Load data results for 60 epochs
fungi_cnn_gru_train_60epochs <- data.table::fread("../../../../../results/secreted_data_run_manually/fungi/df_results_train_cnn_gru_best_fungi_60epochs.csv")
fungi_cnn_gru_val_60epochs <- data.table::fread("../../../../../results/secreted_data_run_manually/fungi/df_results_val_cnn_gru_best_fungi_60epochs.csv")
fungi_cnn_gru_test_60epochs <- data.table::fread("../../../../../results/secreted_data_run_manually/fungi/df_results_test_cnn_gru_best_fungi_60epochs.csv")

# Load data results for 100 epochs
fungi_cnn_gru_train_100epochs <- data.table::fread("../../../../../results/secreted_data_run_manually/fungi/df_results_train_cnn_gru_best_fungi_100epochs.csv")
fungi_cnn_gru_val_100epochs <- data.table::fread("../../../../../results/secreted_data_run_manually/fungi/df_results_val_cnn_gru_best_fungi_100epochs.csv")
fungi_cnn_gru_test_100epochs <- data.table::fread("../../../../../results/secreted_data_run_manually/fungi/df_results_test_cnn_gru_best_fungi_100epochs.csv")
```

```{r}
# Adding the average for the training models with 60 epochs
fungi_cnn_gru_train_60epochs <- fungi_cnn_gru_train_60epochs %>% 
  dplyr::mutate(AVG_CV = rowMeans(.[,2:6]))

fungi_cnn_gru_val_60epochs <- fungi_cnn_gru_val_60epochs %>% 
  dplyr::mutate(AVG_CV =rowMeans(.[,2:6]))

# Adding the average for the training models with 100 epochs
fungi_cnn_gru_train_100epochs <- fungi_cnn_gru_train_100epochs %>% 
  dplyr::mutate(AVG_CV = rowMeans(.[,2:6]))

fungi_cnn_gru_val_100epochs <- fungi_cnn_gru_val_100epochs %>% 
  dplyr::mutate(AVG_CV =rowMeans(.[,2:6]))
```

```{r}
# Results with 60 epochs
get_gg_acc(fungi_cnn_gru_train_60epochs, fungi_cnn_gru_val_60epochs) +
   facet_wrap(~CV, nrow = 2)
```

```{r}
# Results with 60 epochs
get_gg_acc(fungi_cnn_gru_train_100epochs, fungi_cnn_gru_val_100epochs) +
   facet_wrap(~CV, nrow = 2)
```


#### Comparing three prediction results on the test data with different epochs

```{r}
diff_epochs <- rbind(fungi_cnn_gru_test_30epochs  %>% 
  dplyr::select(V1, acc) %>% 
    dplyr::mutate(epochs = 30),
  fungi_cnn_gru_test_60epochs  %>% 
  dplyr::select(V1, acc)  %>% 
    dplyr::mutate(epochs = 60), 
  fungi_cnn_gru_test_100epochs  %>% 
  dplyr::select(V1, acc)  %>% 
    dplyr::mutate(epochs = 100))

plot_comparison(diff_epochs , V1, acc, epochs, show_label = TRUE, label_digits = 3) 
```


From the results above, as we can see, the longer we train the data, the hinger the gap between training accuracy and validation accuracy, meaning the model is overfitting here. 

#### Change the value of regularion rate from `0.001 to 0.01`

```{r}
# Load data for 30 epochs
cnn_gru_train_60epochs_regrate001 <- data.table::fread("../../../../../results/secreted_data_run_manually/fungi/df_results_train_cnn_gru_best_fungi_60epochs_regrate001.csv")
cnn_gru_val_60epochs_regrate001 <- data.table::fread("../../../../../results/secreted_data_run_manually/fungi/df_results_val_cnn_gru_best_fungi_60epochs_regrate001.csv")
cnn_gru_test_60epochs_regrate001 <- data.table::fread("../../../../../results/secreted_data_run_manually/fungi/df_results_test_cnn_gru_best_fungi_60epochs_regrate001.csv")


# Adding the average on the table 

cnn_gru_train_60epochs_regrate001 <- cnn_gru_train_60epochs_regrate001 %>% 
  dplyr::mutate(AVG_CV = rowMeans(.[,2:6]))

cnn_gru_val_60epochs_regrate001 <- cnn_gru_val_60epochs_regrate001 %>% 
  dplyr::mutate(AVG_CV =rowMeans(.[,2:6]))

get_gg_acc(cnn_gru_train_60epochs_regrate001, cnn_gru_val_60epochs_regrate001) +
   facet_wrap(~CV, nrow = 2)
```


```{r}
# Results with 60 epochs
get_gg_acc(fungi_cnn_gru_train_60epochs, fungi_cnn_gru_val_60epochs) +
   facet_wrap(~CV, nrow = 2)
```


#### Comparing the prediction results with different regularization rate

```{r}
compare_test_pred <- fungi_cnn_gru_test_60epochs %>% 
  dplyr::select(V1, acc) %>% 
  mutate(Regrate = "0.001") %>% 
  rbind(cnn_gru_test_60epochs_regrate001 %>% 
          dplyr::select(V1, acc) %>% 
          mutate(Regrate = "0.01")) %>% 
  `colnames<-` (c("CV", "acc", "regrate"))
```


```{r}
plot_comparison(
  data = compare_test_pred ,
  x_var = CV,
  y_var = acc,
  group_var = regrate
)
```

Chnaging the filter to have higher filter 

simple_CNN_GRU(filter_conv = 16,
			                     kernel_size = 1,
			                     maxpool_size = 2,
			                     activation_conv = None,
			                     gru_hidden_units = 8,
                           opt_dropout = 0,
                           opt_dropout_recurrent = 0,
                           opt_go_backwards = 'TRUE',
                           reg_rate = 0.01,
			                     optimizers = 'Adam')
			                     
epochs = 16

```{r}
fungi_cnn_gru_train_filterconv16 <- data.table::fread("../../../../../results/secreted_data_run_manually/fungi/df_results_train_cnn_gru_best_fungi_60epochs_filterconv16.csv")
fungi_cnn_gru_val_filterconv16 <- data.table::fread("../../../../../results/secreted_data_run_manually/fungi/df_results_val_cnn_gru_best_fungi_60epochs_filterconv16.csv")
fungi_cnn_gru_test_filterconv16 <- data.table::fread("../../../../../results/secreted_data_run_manually/fungi/df_results_test_cnn_gru_best_fungi_60epochs_filterconv16.csv")


fungi_cnn_gru_train_filterconv16 <- fungi_cnn_gru_train_filterconv16 %>% 
  mutate(AVG_CV = rowMeans(.[,2:6]))

fungi_cnn_gru_val_filterconv16 <- fungi_cnn_gru_val_filterconv16 %>% 
  mutate(AVG_CV = rowMeans(.[,2:6]))
```


```{r}
get_gg_acc(fungi_cnn_gru_train_filterconv16, fungi_cnn_gru_val_filterconv16) +
   facet_wrap(~CV, nrow = 2)
```



It seems if we are using filter convolution = 16, it is more overfitting than using only 8. Therefore, we will stick with filter conv = 8. And now I am going to introduce dropout to the system, using the 

```{r}
fungi_cnn_gru_train_filterconv8_drop025 <- data.table::fread("../../../../../results/secreted_data_run_manually/fungi/df_results_train_cnn_gru_best_fungi_60epochs_filterconv8_drop025.csv")

fungi_cnn_gru_val_filterconv8_drop025 <- data.table::fread("../../../../../results/secreted_data_run_manually/fungi/df_results_val_cnn_gru_best_fungi_60epochs_filterconv8_drop025.csv")

fungi_cnn_gru_test_filterconv8_drop025 <- data.table::fread("../../../../../results/secreted_data_run_manually/fungi/df_results_test_cnn_gru_best_fungi_60epochs_filterconv8_drop025.csv")


fungi_cnn_gru_train_filterconv8_drop025 <- fungi_cnn_gru_train_filterconv8_drop025 %>% 
  mutate(AVG_CV = rowMeans(.[,2:6]))

fungi_cnn_gru_val_filterconv8_drop025 <- fungi_cnn_gru_val_filterconv8_drop025 %>% 
  mutate(AVG_CV = rowMeans(.[,2:6]))
```

```{r}
get_gg_acc(fungi_cnn_gru_train_filterconv8_drop025, fungi_cnn_gru_val_filterconv8_drop025) +
   facet_wrap(~CV, nrow = 2)
```

```{r}
fungi_cnn_gru_test_filterconv8_drop025
```

```{r}
fungi_cnn_gru_test_60epochs
```

```{r}
compare_test_pred_with_diff_dropout <- fungi_cnn_gru_test_60epochs %>% 
  dplyr::select(V1, acc) %>% 
  mutate(Dropout = 0) %>% 
  rbind(fungi_cnn_gru_test_filterconv8_drop025 %>% 
          dplyr::select(V1, acc) %>% 
          mutate(Dropout = 0.25)) %>% 
  `colnames<-` (c("CV", "Acc", "Dropout"))
```


```{r}
plot_comparison(
  data = compare_test_pred_with_diff_dropout,
  x_var = CV,
  y_var = Acc,
  group_var = Dropout
)
```

## GRU - Embedding

```{r}
fungi_gru_embeding_all <- data.table::fread("../../../../../data/secreted_data/training-results/fungi/fungi_scan_results_gru_embedding_scan_fungi.csv") %>% 
  select(params, mean_test_score)

fungi_gru_embeding_all %>% 
  # dplyr::filter(params == "{‘reg_rate’: 0.001, ‘outputdim’: 16, ‘optimizers’: ‘Adam’, ‘opt_go_backwards’: ‘FALSE’, ‘opt_dropout_recurrent’: 0, ‘opt_dropout’: 0, ‘gru_hidden_units’: 32, ‘epochs’: 30, ‘batch_size’: 8}") %>% 
  dplyr::arrange(desc(mean_test_score)) %>%
  head(20) %>% 
  knitr::kable()
```

```{r}
fungi_gru_embeding_all_pred <- data.table::fread("../../../../../data/secreted_data/training-results/fungi/df_pred_results_gru_embedding_scan_fungi.csv") 

fungi_gru_embeding_all_pred %>% 
  dplyr::arrange(desc(Accuracy)) %>% 
  knitr::kable()
```

### Manually running 

```{r}
fungi_gru_emb_train <-  data.table::fread("../../../../../results/secreted_data_run_manually/fungi/df_results_train_gru_emb_best_fungi.csv")
fungi_gru_emb_val <- data.table::fread("../../../../../results/secreted_data_run_manually/fungi/df_results_val_gru_emb_best_fungi.csv")


# Get the avergae of the acc for each cross validation
fungi_gru_emb_train <- fungi_gru_emb_train %>% 
  mutate(AVG_CV = rowMeans(.[,2:6]))

fungi_gru_emb_val <- fungi_gru_emb_val %>% 
  mutate(AVG_CV = rowMeans(.[,2:6]))
```


```{r}
get_gg_acc(fungi_gru_emb_train, fungi_gru_emb_val) +
   facet_wrap(~CV, nrow = 2)
```

As we can see, it seems that the training need more epochs

```{r}
fungi_gru_emb_test <- data.table::fread("../../../../../results/secreted_data_run_manually/fungi/df_results_test_gru_emb_best_fungi.csv")

fungi_gru_emb_test %>% 
  knitr::kable()
```


More epochs:

```{r}
fungi_gru_emb_train_60epochs <-  data.table::fread("../../../../../results/secreted_data_run_manually/fungi/df_results_train_gru_emb_best_fungi_60epochs.csv")
fungi_gru_emb_val_60epochs <- data.table::fread("../../../../../results/secreted_data_run_manually/fungi/df_results_val_gru_emb_best_fungi_60epochs.csv")
fungi_gru_emb_test_60epochs <- data.table::fread("../../../../../results/secreted_data_run_manually/fungi/df_results_test_gru_emb_best_fungi_60epochs.csv")



# Get the avergae of the acc for each cross validation
fungi_gru_emb_train_60epochs <- fungi_gru_emb_train_60epochs %>% 
  mutate(AVG_CV = rowMeans(.[,2:6]))

fungi_gru_emb_val_60epochs <- fungi_gru_emb_val_60epochs %>% 
  mutate(AVG_CV = rowMeans(.[,2:6]))
```


```{r}
get_gg_acc(fungi_gru_emb_train_60epochs, fungi_gru_emb_val_60epochs) +
   facet_wrap(~CV, nrow = 2)
```

```{r}
fungi_gru_emb_compare <- rbind(fungi_gru_emb_test %>% 
  dplyr::select(V1, acc) %>% 
    dplyr::mutate(epochs = 30), 
fungi_gru_emb_test_60epochs %>% 
    dplyr::select(V1, acc) %>% 
    dplyr::mutate(epochs = 60))

plot_comparison(fungi_gru_emb_compare, V1, acc, epochs, show_label = TRUE, label_digits = 3) 
```


## LSTM-Embedding

```{r}
fungi_lstm_emb <- data.table::fread("../../../../../data/secreted_data/training-results/fungi/all_scan_results_lstm_emb_scan_fungi.csv") %>% 
  dplyr::select(params, mean_test_score)

fungi_lstm_emb %>% 
  dplyr::arrange(desc(mean_test_score)) %>% 
  knitr::kable()
```

### Manually running 

```{r}
fungi_lstm_emb_train <-  data.table::fread("../../../../../results/secreted_data_run_manually/fungi/df_results_train_lstm_emb_fungi.csv")
fungi_lstm_emb_val <- data.table::fread("../../../../../results/secreted_data_run_manually/fungi/df_results_val_lstm_emb_fungi.csv")
fungi_lstm_emb_test <- data.table::fread("../../../../../results/secreted_data_run_manually/fungi/df_results_test_lstm_emb_fungi.csv")


# Get the avergae of the acc for each cross validation
fungi_lstm_emb_train <- fungi_lstm_emb_train %>% 
  mutate(AVG_CV = rowMeans(.[,2:6]))

fungi_lstm_emb_val <- fungi_lstm_emb_val %>% 
  mutate(AVG_CV = rowMeans(.[,2:6]))

fungi_lstm_emb_test %>% 
  knitr::kable()
```

```{r}
get_gg_acc(fungi_lstm_emb_train, fungi_lstm_emb_val) +
   facet_wrap(~CV, nrow = 2)
```

```{r}
fungi_lstm_emb_train_60epochs <-  data.table::fread("../../../../../results/secreted_data_run_manually/fungi/df_results_train_lstm_emb_fungi_60epochs.csv")
fungi_lstm_emb_val_60epochs <-  data.table::fread("../../../../../results/secreted_data_run_manually/fungi/df_results_val_lstm_emb_fungi_60epochs.csv")
fungi_lstm_emb_test_60epochs <-  data.table::fread("../../../../../results/secreted_data_run_manually/fungi/df_results_test_lstm_emb_fungi_60epochs.csv")

# Get the avergae of the acc for each cross validation
fungi_lstm_emb_train_60epochs <- fungi_lstm_emb_train_60epochs %>% 
  mutate(AVG_CV = rowMeans(.[,2:6]))

fungi_lstm_emb_val_60epochs <- fungi_lstm_emb_val_60epochs %>% 
  mutate(AVG_CV = rowMeans(.[,2:6]))
```

```{r}
get_gg_acc(fungi_lstm_emb_train_60epochs, fungi_lstm_emb_val_60epochs) +
   facet_wrap(~CV, nrow = 2)
```

```{r}
fungi_lstm_emb_test_60epochs %>% 
  knitr::kable()
```

Making comparison on the test data 

```{r}
fungi_lstm_emb_compare <- rbind(fungi_lstm_emb_test %>% 
  dplyr::select(V1, acc) %>% 
    dplyr::mutate(epochs = 30), 
 fungi_lstm_emb_test_60epochs %>% 
    dplyr::select(V1, acc) %>% 
    dplyr::mutate(epochs = 60))
```

```{r}
plot_comparison(fungi_lstm_emb_compare, V1, acc, epochs, show_label = TRUE, label_digits = 3) 
```


## CNN-LSTM 

```{r}
cnn_lstm_file <- "../../../../../data/secreted_data/training-results/fungi/0003-cnn-lstm-scan-fungi-secreted.log"
cnn_lstm_params_list <- c(
  "strides", "padding", "optimizers", "number_hidden_units",
  "filters_LSTM", "filters", 
  "batch_size", "activation_convolution", "activation_LSTM", "epochs"
)
cnn_lstm_numeric_params <- c(
  "strides", "number_hidden_units", "filters_LSTM",
  "filters", "epochs", "batch_size"
)
```


```{r}
cnn_lstm_log_data_raw <- cnn_lstm_file %>%
  parscanlogreader::read_raw_log() %>%
  parscanlogreader::clean_log_data()

cnn_lstm_log_data <- cnn_lstm_log_data_raw %>%
  parscanlogreader::summarise_log_data() %>% 
  dplyr::arrange(desc(acc_mean)) %>% 
  tidyr::drop_na()
```


```{r}
cnn_lstm_log_data %>%
  head(10) %>% 
  knitr::kable()
```

By getting the best value, we can then use the best combination of hyperparameter setting above to train manually. 

```{r}
fungi_cnn_lstm_train <- data.table::fread("../../../../../results/secreted_data_run_manually/fungi/df_results_train_cnn_lstm_best_fungi.csv")
fungi_cnn_lstm_val <- data.table::fread("../../../../../results/secreted_data_run_manually/fungi/df_results_val_cnn_lstm_best_fungi.csv")
fungi_cnn_lstm_test <-  data.table::fread("../../../../../results/secreted_data_run_manually/fungi/df_results_test_cnn_lstm_best_fungi.csv")

fungi_cnn_lstm_train <- fungi_cnn_lstm_train %>% 
  mutate(AVG_CV = rowMeans(.[,2:6]))

fungi_cnn_lstm_val <- fungi_cnn_lstm_val %>% 
  mutate(AVG_CV = rowMeans(.[,2:6]))

get_gg_acc(fungi_cnn_lstm_train, fungi_cnn_lstm_val) +
   facet_wrap(~CV, nrow = 2)
```

```{r}
fungi_cnn_lstm_train_filter8_filterlstm8 <- data.table::fread("../../../../../results/secreted_data_run_manually/fungi/df_results_train_cnn_lstm_best_fungi_filter8_filterlstm8.csv")
fungi_cnn_lstm_val_filter8_filterlstm8 <- data.table::fread("../../../../../results/secreted_data_run_manually/fungi/df_results_val_cnn_lstm_best_fungi_filter8_filterlstm8.csv")
fungi_cnn_lstm_test_filter8_filterlstm8 <-  data.table::fread("../../../../../results/secreted_data_run_manually/fungi/df_results_test_cnn_lstm_best_fungi_filter8_filterlstm8.csv")

fungi_cnn_lstm_train_filter8_filterlstm8 <- fungi_cnn_lstm_train_filter8_filterlstm8 %>% 
  mutate(AVG_CV = rowMeans(.[,2:6]))

fungi_cnn_lstm_val_filter8_filterlstm8 <- fungi_cnn_lstm_val_filter8_filterlstm8 %>% 
  mutate(AVG_CV = rowMeans(.[,2:6]))

get_gg_acc(fungi_cnn_lstm_train_filter8_filterlstm8, fungi_cnn_lstm_val_filter8_filterlstm8 ) +
   facet_wrap(~CV, nrow = 2)
```


#### Comparing the prediction results with different regularization rate

```{r}
compare_test_cnn_lstm <- fungi_cnn_lstm_test %>% 
  dplyr::select(V1, acc) %>% 
  mutate(filter = "16") %>% 
  rbind(fungi_cnn_lstm_test_filter8_filterlstm8%>% 
          dplyr::select(V1, acc) %>% 
          mutate(filter = "8")) %>% 
  `colnames<-` (c("CV", "acc", "filter"))
```


```{r}
plot_comparison(
  data = compare_test_cnn_lstm,
  x_var = CV,
  y_var = acc,
  group_var = filter
)
```

Another experiment: trying to run both case longer like 60 epochs, and see how the reults will be, either it will be super overfitting for both or not. 

```{r}
fungi_cnn_lstm_train_filter8_filterlstm8_60epochs <- data.table::fread("../../../../../results/secreted_data_run_manually/fungi/df_results_train_cnn_lstm_best_fungi_filter8_filterlstm8_epochs60.csv")
fungi_cnn_lstm_val_filter8_filterlstm8_60epochs <- data.table::fread("../../../../../results/secreted_data_run_manually/fungi/df_results_val_cnn_lstm_best_fungi_filter8_filterlstm8_epochs60.csv")
fungi_cnn_lstm_test_filter8_filterlstm8_60epochs <-  data.table::fread("../../../../../results/secreted_data_run_manually/fungi/df_results_test_cnn_lstm_best_fungi_filter8_filterlstm8_epochs60.csv")

fungi_cnn_lstm_train_filter8_filterlstm8_60epochs <- fungi_cnn_lstm_train_filter8_filterlstm8_60epochs %>% 
  mutate(AVG_CV = rowMeans(.[,2:6]))

fungi_cnn_lstm_val_filter8_filterlstm8_60epochs <- fungi_cnn_lstm_val_filter8_filterlstm8_60epochs  %>% 
  mutate(AVG_CV = rowMeans(.[,2:6]))

get_gg_acc(fungi_cnn_lstm_train_filter8_filterlstm8_60epochs, fungi_cnn_lstm_val_filter8_filterlstm8_60epochs) +
   facet_wrap(~CV, nrow = 2)
```

We can change the number of bacth to 16


```{r}
fungi_cnn_lstm_train_filter8_filterlstm8_batch16 <- data.table::fread("../../../../../results/secreted_data_run_manually/fungi/df_results_train_cnn_lstm_best_fungi_filter8_filterlstm8_batch16.csv")
fungi_cnn_lstm_val_filter8_filterlstm8_batch16 <- data.table::fread("../../../../../results/secreted_data_run_manually/fungi/df_results_val_cnn_lstm_best_fungi_filter8_filterlstm8_batch16.csv")
fungi_cnn_lstm_test_filter8_filterlstm8_batch16 <-  data.table::fread("../../../../../results/secreted_data_run_manually/fungi/df_results_test_cnn_lstm_best_fungi_filter8_filterlstm8_batch16.csv")


fungi_cnn_lstm_train_filter8_filterlstm8_batch16 <- fungi_cnn_lstm_train_filter8_filterlstm8_batch16 %>% 
  mutate(AVG_CV = rowMeans(.[,2:6]))

fungi_cnn_lstm_val_filter8_filterlstm8_batch16 <- fungi_cnn_lstm_val_filter8_filterlstm8_batch16  %>% 
  mutate(AVG_CV = rowMeans(.[,2:6]))

get_gg_acc(fungi_cnn_lstm_train_filter8_filterlstm8_batch16, fungi_cnn_lstm_val_filter8_filterlstm8_batch16) +
   facet_wrap(~CV, nrow = 2)
```

