---
title: "Untitled"
author: "Ruth Kristianingsih"
date: "17/02/2020"
knit: (function(inputFile, encoding) { rmarkdown::render(inputFile, encoding = encoding, output_dir = here::here("reports", stringr::str_remove(getwd(), here::here("scripts/r-scripts/")))) })
output:
  md_document:
    variant: markdown_github
---


# Manually tuning model for Oomycete

## Background

In this report, manually tuning model for oomycete will be perfomed.

## Load library

```{r setup, include = FALSE}
library(tidyverse)
library(patchwork)
source("../../../r-functions/plot_training_vs_validation.R")
```

## Hyperparameter Scan Results

```{r}
oomycete_cnn_gru_secreted <- data.table::fread("../../../../../data/secreted_data/training-results/oomycete/results/secreted_hyper_scan/df_pred_results_cnn_gru_scan_oomycete_secreted.csv")

oomycete_cnn_gru_secreted %>% 
  arrange(desc(Accuracy)) %>% 
  head(6) %>% 
  knitr::kable()
```


### CNN-GRU

```{r}
# Load the results data od oomycete with only 30 epochs
oomycete_cnn_gru_train_30epochs <- data.table::fread("../../../../../results/secreted_data_run_manually/oomycete/df_results_train_cnn_gru_best_oomycete_30epochs.csv")
oomycete_cnn_gru_val_30epochs <- data.table::fread("../../../../../results/secreted_data_run_manually/oomycete/df_results_val_cnn_gru_best_oomycete_30epochs.csv")
oomycete_cnn_gru_test_30epochs <- data.table::fread("../../../../../results/secreted_data_run_manually/oomycete/df_results_test_cnn_gru_best_oomycete_30epochs.csv")
```


```{r}
get_gg_acc(oomycete_cnn_gru_train_30epochs, oomycete_cnn_gru_val_30epochs) +
   facet_wrap(~CV, nrow = 2)
```

```{r}
# Load the results data od oomycete with 50 epochs
oomycete_cnn_gru_train_50epochs <- data.table::fread("../../../../../results/secreted_data_run_manually/oomycete/df_results_train_cnn_gru_best_oomycete_50epochs.csv")
oomycete_cnn_gru_val_50epochs <- data.table::fread("../../../../../results/secreted_data_run_manually/oomycete/df_results_val_cnn_gru_best_oomycete_50epochs.csv")
oomycete_cnn_gru_test_50epochs <- data.table::fread("../../../../../results/secreted_data_run_manually/oomycete/df_results_test_cnn_gru_best_oomycete_50epochs.csv")
```

```{r}
get_gg_acc(oomycete_cnn_gru_train_50epochs, oomycete_cnn_gru_val_50epochs) +
   facet_wrap(~CV, nrow = 2)
```


Making comparison on the test data 

```{r}
oomycete_compare <- rbind(oomycete_cnn_gru_test_30epochs %>% 
  dplyr::select(V1, acc) %>% 
    dplyr::mutate(epochs = 30), 
  oomycete_cnn_gru_test_50epochs %>% 
    dplyr::select(V1, acc) %>% 
    dplyr::mutate(epochs = 50))
```

```{r}
plot_comparison(oomycete_compare, V1, acc, epochs, show_label = TRUE, label_digits = 3) 
```

#### Take the second best model

```{r}
# Load the results data od oomycete with 50 epochs
oomycete_cnn_gru_train_secondbest <- data.table::fread("../../../../../results/secreted_data_run_manually/oomycete/df_results_train_cnn_gru_best_second_oomycete.csv")
oomycete_cnn_gru_val_secondbest <- data.table::fread("../../../../../results/secreted_data_run_manually/oomycete/df_results_val_cnn_gru_best_second_oomycete.csv")
oomycete_cnn_gru_test_secondbest <- data.table::fread("../../../../../results/secreted_data_run_manually/oomycete/df_results_test_cnn_gru_best_second_oomycete.csv")
```

```{r}
get_gg_acc(oomycete_cnn_gru_train_secondbest, oomycete_cnn_gru_val_secondbest) +
   facet_wrap(~CV, nrow = 2)
```

Now, using the dropout 0.5, get the result:

```{r}
# Load the results data od oomycete with 50 epochs
oomycete_cnn_gru_train_secondbest_drop05 <- data.table::fread("../../../../../results/secreted_data_run_manually/oomycete/df_results_train_cnn_gru_best_second_oomycete_drop05.csv")
oomycete_cnn_gru_val_secondbest_drop05 <- data.table::fread("../../../../../results/secreted_data_run_manually/oomycete/df_results_val_cnn_gru_best_second_oomycete_drop05.csv")
oomycete_cnn_gru_test_secondbest_drop05 <- data.table::fread("../../../../../results/secreted_data_run_manually/oomycete/df_results_test_cnn_gru_best_second_oomycete_drop05.csv")
```

```{r}
get_gg_acc(oomycete_cnn_gru_train_secondbest_drop05, oomycete_cnn_gru_val_secondbest_drop05) +
   facet_wrap(~CV, nrow = 2)
```

Making comparison on the test data 

```{r}
oomycete_compare_secondbest <- rbind(oomycete_cnn_gru_test_secondbest %>% 
  dplyr::select(V1, acc) %>% 
    dplyr::mutate(dropout = 0), 
  oomycete_cnn_gru_test_secondbest_drop05 %>% 
    dplyr::select(V1, acc) %>% 
    dplyr::mutate(dropout = 0.5))
```

```{r}
plot_comparison(oomycete_compare_secondbest, V1, acc, dropout, show_label = TRUE, label_digits = 3) 
```

#### Take the third best model

```{r}
oomycete_cnn_gru_third_model_train <- data.table::fread("../../../../../results/secreted_data_run_manually/oomycete/df_results_train_cnn_gru_best_third_oomycete_batch8.csv")
oomycete_cnn_gru_third_model_val <- data.table::fread("../../../../../results/secreted_data_run_manually/oomycete/df_results_val_cnn_gru_best_third_oomycete_batch8.csv")
oomycete_cnn_gru_third_model_test <- data.table::fread("../../../../../results/secreted_data_run_manually/oomycete/df_results_test_cnn_gru_best_third_oomycete_batch8.csv")


get_gg_acc(oomycete_cnn_gru_third_model_train, oomycete_cnn_gru_third_model_val) +
   facet_wrap(~CV, nrow = 2)
```

#### Take the fifth best model

```{r}
oomycete_cnn_gru_fifth_model_train <- data.table::fread("../../../../../results/secreted_data_run_manually/oomycete/df_results_train_cnn_gru_best_fifth.csv")
oomycete_cnn_gru_fifth_model_val <- data.table::fread("../../../../../results/secreted_data_run_manually/oomycete/df_results_val_cnn_gru_best_fifth.csv")
oomycete_cnn_gru_fifth_model_test <- data.table::fread("../../../../../results/secreted_data_run_manually/oomycete/df_results_test_cnn_gru_best_fifth.csv")


get_gg_acc(oomycete_cnn_gru_fifth_model_train, oomycete_cnn_gru_fifth_model_val) +
   facet_wrap(~CV, nrow = 2)
```

Bt decreasing the number of filter convolution to 8, it is hopfefully can decrease the overfitting

```{r}
oomycete_cnn_gru_fifth_model_train_filter8 <- data.table::fread("../../../../../results/secreted_data_run_manually/oomycete/df_results_train_cnn_gru_best_fifth_filter8.csv")
oomycete_cnn_gru_fifth_model_val_filter8 <- data.table::fread("../../../../../results/secreted_data_run_manually/oomycete/df_results_val_cnn_gru_best_fifth_filter8.csv")
oomycete_cnn_gru_fifth_model_test_filter8 <- data.table::fread("../../../../../results/secreted_data_run_manually/oomycete/df_results_test_cnn_gru_best_fifth_filter8.csv")


get_gg_acc(oomycete_cnn_gru_fifth_model_train_filter8, oomycete_cnn_gru_fifth_model_val_filter8) +
   facet_wrap(~CV, nrow = 2)
```

#### Comparing the evaluation on the test data 

```{r}
oomycete_compare_fifthbest <- rbind(oomycete_cnn_gru_fifth_model_test %>% 
  dplyr::select(V1, acc) %>% 
    dplyr::mutate(filters = 16), 
  oomycete_cnn_gru_fifth_model_test_filter8 %>% 
    dplyr::select(V1, acc) %>% 
    dplyr::mutate(filters = 8))
```

```{r}
plot_comparison(oomycete_compare_fifthbest, V1, acc, filters, show_label = TRUE, label_digits = 3) 
```



### CNN-LSTM

```{r}
oomycete_cnn_lstm_secreted <- data.table::fread("../../../../../data/secreted_data/training-results/oomycete/results/secreted_hyper_scan/df_pred_results_cnn_lstm_scan_oomycete_secreted_data.csv")


oomycete_cnn_lstm_secreted %>% 
  arrange(desc(Accuracy)) %>% 
  head(5) %>% 
  knitr::kable()
```

#### Manually tuning for the fourth model 

{‘strides’: 1, ‘padding’: ‘valid’, ‘optimizers’: ‘Adam’, ‘number_hidden_units’: 8, ‘filters_LSTM’: 4, ‘filters’: 8, ‘epochs’: 30, ‘batch_size’: 8, ‘activation_convolution’: None, ‘activation_LSTM’: ‘tanh’}

```{r}
oomycete_cnn_lstm_fourth_model_train <- data.table::fread("../../../../../results/secreted_data_run_manually/oomycete/df_results_train_cnn_lstm_best_oomycete.csv")
oomycete_cnn_lstm_fourth_model_val <- data.table::fread("../../../../../results/secreted_data_run_manually/oomycete/df_results_val_cnn_lstm_best_oomycete.csv")
oomycete_cnn_lstm_fourth_model_test <- data.table::fread("../../../../../results/secreted_data_run_manually/oomycete/df_results_test_cnn_lstm_best_oomycete.csv")

oomycete_cnn_lstm_fourth_model_train <- oomycete_cnn_lstm_fourth_model_train %>% 
  dplyr::mutate(AVG_CV =rowMeans(.[,2:6]))

oomycete_cnn_lstm_fourth_model_val <- oomycete_cnn_lstm_fourth_model_val %>% 
  dplyr::mutate(AVG_CV =rowMeans(.[,2:6]))


get_gg_acc(oomycete_cnn_lstm_fourth_model_train, oomycete_cnn_lstm_fourth_model_val) +
   facet_wrap(~CV, nrow = 2)
```


more epochs on CNN-LSTM

```{r}
oomycete_cnn_lstm_60epochs_train <- data.table::fread("../../../../../results/secreted_data_run_manually/oomycete/df_results_train_cnn_lstm_best_oomycete_60epochs.csv")
oomycete_cnn_lstm_60epochs_val <- data.table::fread("../../../../../results/secreted_data_run_manually/oomycete/df_results_val_cnn_lstm_best_oomycete_60epochs.csv")
oomycete_cnn_lstm_60epochs_test <- data.table::fread("../../../../../results/secreted_data_run_manually/oomycete/df_results_test_cnn_lstm_best_oomycete_60epochs.csv")


oomycete_cnn_lstm_60epochs_train <- oomycete_cnn_lstm_60epochs_train %>% 
  dplyr::mutate(AVG_CV =rowMeans(.[,2:6]))

oomycete_cnn_lstm_60epochs_val <- oomycete_cnn_lstm_60epochs_val %>% 
  dplyr::mutate(AVG_CV =rowMeans(.[,2:6]))

get_gg_acc(oomycete_cnn_lstm_60epochs_train, oomycete_cnn_lstm_60epochs_val) +
   facet_wrap(~CV, nrow = 2)
```

```{r}
oomycete_cnn_lstm_60epochs_test
```

#### Comparing the evaluation on the test data 

```{r}
oomycete_compare_fouthmodel <- rbind(oomycete_cnn_lstm_fourth_model_test %>% 
  dplyr::select(V1, acc) %>% 
    dplyr::mutate(epochs = 30), 
  oomycete_cnn_lstm_60epochs_test %>% 
    dplyr::select(V1, acc) %>% 
    dplyr::mutate(epochs = 60))
```

```{r}
plot_comparison(oomycete_compare_fouthmodel, V1, acc, epochs, show_label = TRUE, label_digits = 3) 
```

### LSTM-Emb

```{r}
oomycete_lstm_emb_train <- data.table::fread("../../../../../results/secreted_data_run_manually/oomycete/df_results_train_lstm_emb_oomycete.csv")
oomycete_lstm_emb_val <- data.table::fread("../../../../../results/secreted_data_run_manually/oomycete/df_results_val_lstm_emb_oomycete.csv")
oomycete_lstm_emb_test <- data.table::fread("../../../../../results/secreted_data_run_manually/oomycete/df_results_test_lstm_emb_oomycete.csv")

oomycete_lstm_emb_train <- oomycete_lstm_emb_train %>% 
  dplyr::mutate(AVG_CV =rowMeans(.[,2:6]))

oomycete_lstm_emb_val  <- oomycete_lstm_emb_val  %>% 
  dplyr::mutate(AVG_CV =rowMeans(.[,2:6]))


get_gg_acc(oomycete_lstm_emb_train, oomycete_lstm_emb_val) +
   facet_wrap(~CV, nrow = 2)
```

```{r}
oomycete_lstm_emb_train <- data.table::fread("../../../../../results/secreted_data_run_manually/oomycete/df_results_train_lstm_emb_oomycete_lstm16.csv")
oomycete_lstm_emb_val <- data.table::fread("../../../../../results/secreted_data_run_manually/oomycete/df_results_val_lstm_emb_oomycete_lstm16.csv")
oomycete_lstm_emb_test <- data.table::fread("../../../../../results/secreted_data_run_manually/oomycete/df_results_test_lstm_emb_oomycete_lstm16.csv")

oomycete_lstm_emb_train <- oomycete_lstm_emb_train %>% 
  dplyr::mutate(AVG_CV =rowMeans(.[,2:6]))

oomycete_lstm_emb_val  <- oomycete_lstm_emb_val  %>% 
  dplyr::mutate(AVG_CV =rowMeans(.[,2:6]))


get_gg_acc(oomycete_lstm_emb_train, oomycete_lstm_emb_val) +
   facet_wrap(~CV, nrow = 2)
```

Reduce the size of the filter from 32 to 16, and we will see what happened:

```{r}
oomycete_lstm_emb_train <- data.table::fread("../../../../../results/secreted_data_run_manually/oomycete/df_results_train_lstm_emb_oomycete_lstm16_outputdim_32.csv")
oomycete_lstm_emb_val <- data.table::fread("../../../../../results/secreted_data_run_manually/oomycete/df_results_val_lstm_emb_oomycete_lstm16_outputdim_32.csv")
oomycete_lstm_emb_test <- data.table::fread("../../../../../results/secreted_data_run_manually/oomycete/df_results_test_lstm_emb_oomycete_lstm16_outputdim_32.csv")

oomycete_lstm_emb_train <- oomycete_lstm_emb_train %>% 
  dplyr::mutate(AVG_CV =rowMeans(.[,2:6]))

oomycete_lstm_emb_val  <- oomycete_lstm_emb_val  %>% 
  dplyr::mutate(AVG_CV =rowMeans(.[,2:6]))


get_gg_acc(oomycete_lstm_emb_train, oomycete_lstm_emb_val) +
   facet_wrap(~CV, nrow = 2)
```



### GRU-Emb

```{r}
oomycete_gru_emb_train <- data.table::fread("../../../../../results/secreted_data_run_manually/oomycete/df_results_train_gru_emb_oomycete.csv")
oomycete_gru_emb_val <- data.table::fread("../../../../../results/secreted_data_run_manually/oomycete/df_results_val_gru_emb_oomycete.csv")
oomycete_gru_emb_test <- data.table::fread("../../../../../results/secreted_data_run_manually/oomycete/df_results_test_gru_emb_oomycete.csv")

oomycete_gru_emb_train <- oomycete_gru_emb_train %>% 
  dplyr::mutate(AVG_CV =rowMeans(.[,2:6]))

oomycete_gru_emb_val  <- oomycete_gru_emb_val  %>% 
  dplyr::mutate(AVG_CV =rowMeans(.[,2:6]))

get_gg_acc(oomycete_gru_emb_train, oomycete_gru_emb_val) +
   facet_wrap(~CV, nrow = 2)
```

By training them for more epochs, then now we can read the data:

```{r}
oomycete_gru_emb_train_60epochs <- data.table::fread("../../../../../results/secreted_data_run_manually/oomycete/df_results_train_gru_emb_oomycete_60epochs.csv")
oomycete_gru_emb_val_60epochs <- data.table::fread("../../../../../results/secreted_data_run_manually/oomycete/df_results_val_gru_emb_oomycete_60epochs.csv")
oomycete_gru_emb_test_60epochs <- data.table::fread("../../../../../results/secreted_data_run_manually/oomycete/df_results_test_gru_emb_oomycete_60epochs.csv")

oomycete_gru_emb_train_60epochs <- oomycete_gru_emb_train_60epochs %>% 
  dplyr::mutate(AVG_CV =rowMeans(.[,2:6]))

oomycete_gru_emb_val_60epochs <- oomycete_gru_emb_val_60epochs  %>% 
  dplyr::mutate(AVG_CV =rowMeans(.[,2:6]))

get_gg_acc(oomycete_gru_emb_train_60epochs, oomycete_gru_emb_val_60epochs) +
   facet_wrap(~CV, nrow = 2) +
   theme_light()
```


```{r results = 'asis'}
oomycete_gru_emb_test_60epochs %>% 
  knitr::kable()
```

```{r}
oomycete_compare_gru_emb <- rbind(oomycete_gru_emb_test %>% 
  dplyr::select(V1, acc) %>% 
    dplyr::mutate(epochs = 30), 
  oomycete_gru_emb_test_60epochs %>% 
    dplyr::select(V1, acc) %>% 
    dplyr::mutate(epochs = 60))
```

```{r}
plot_comparison(oomycete_compare_gru_emb, V1, acc, epochs, show_label = TRUE, label_digits = 3) 
```
