---
title: "Untitled"
author: "Ruth Kristianingsih"
date: "29/01/2020"
knit: (function(inputFile, encoding) { rmarkdown::render(inputFile, encoding = encoding, output_dir = here::here("reports", stringr::str_remove(getwd(), here::here("scripts/r-scripts/")))) })
output:
  md_document:
    variant: markdown_github
---

# Re-do the resampling data with BLAST 

## Background

Based on the innefective sampling methods I have done before, I was not effective, since I did not do BLAST while sampling the data, this results on the additional effort to do BLAST while splitting the data which there was no point since if we have identical protein sequences on our dataset, no matter how hard we blast to avoiud identical data between datasets, it will still be identical protein sequences inside (this is useless). 

## Approach

A new way to tackle this issue (not to have identical protein data inside the datasets) are doing BLAST while doing the sampling process. 

## Execution

### Load libraries

```{r setup}
library(tidyverse)
library(dplyr)

# Source functions
source(here::here("scripts/r-scripts/r-functions", "blast_data.R"))
# source(here::here("scripts/r-scripts/r-functions", "dealing_with_df.R"))
source(here::here("scripts/r-scripts/r-functions", "getting_sample_data.R"))
```

### Run with bacteria

#### Load sequence and lookup data

```{r}
# Read the full table of the prediction result of the SignalP
bacteria_full_table <- data.table::fread(here::here("data/secreted_data/updated_signalp_results", "bacteria_full_table.csv")) %>%
  # Make the name of organisms consistent with the lookup table
  dplyr::mutate(
    organism_name = organism_name %>%
      stringr::str_replace_all("^_", "") %>%
      stringr::str_to_lower()
  ) %>%
  dplyr::filter(prediction == "Signal peptide", signalp_prob > 0.9)
```

```{r}
bacteria_lookup_table <- data.table::fread(here::here("data/secreted_data/signalp-pipeline", "bacteria_lookup_table.csv")) %>%
  `colnames<-`(c("Pathogenspecies", "Count")) %>%
  group_by(Pathogenspecies) %>%
  summarise(samples_needed = sum(Count)) %>%
  ungroup()

bacteria_lookup_table <- bacteria_lookup_table %>%
  mutate(
    Pathogenspecies = Pathogenspecies %>%
      stringr::str_to_lower() %>%
      stringr::str_remove_all("\\.") %>%
      stringr::str_replace_all(" ", "_")
  )

bacteria_lookup_table <- bacteria_lookup_table %>%
  # Manual name fixes
  mutate(
    Pathogenspecies = Pathogenspecies %>%
      stringr::str_replace_all("\\(", "") %>%
      stringr::str_replace_all("\\)", "") %>%
      stringr::str_replace_all("-", "_"),
    Pathogenspecies = ifelse(
      Pathogenspecies == "xanthomonas_citri_subsp_malvacearum",
      "xanthomonas_citri_pv_malvacearum",
      Pathogenspecies
    ),
    Pathogenspecies = ifelse(
      Pathogenspecies == "pantoea_stewartii_subsp_stewartii",
      "pantoea_stewartii",
      Pathogenspecies
    )
  ) %>%
  # Fix repeated Pathogenspecies
  group_by(Pathogenspecies) %>%
  summarise(samples_needed = sum(samples_needed))
```

#### Merge sequence data with lookup

```{r}
bacteria_merged_table <- merge_data_with_lookup_table(
  bag_data = bacteria_full_table,
  bag_var = organism_name,
  lookup_data = bacteria_lookup_table,
  lookup_var = Pathogenspecies
)

# Check if the merged table doesn't have any NAs
if (
  length(
    bacteria_merged_table %>%
      filter(samples_needed %>% is.na()) %>%
      pull(organism_name) %>% unique()
  ) == 0
) {
  rm(bacteria_full_table, bacteria_lookup_table)
}
```

#### Sample sequences

```r
bacteria_sampled_table <- bacteria_merged_table %>%
  map_sampleing_function(
    col_organism = organism_name, 
    col_id = ID, 
    col_seq = sequence
  )
```

#### Check quality of samples

We check first if enough samples were obtained compares to the needed samples from the lookup table.

```{r}
# Read the results 

bacteria_sampled_table <- readRDS("../../../data/secreted_data/ready_to_process/sampled_data_without_identical/bacteria_sampled_table_good.RDS")
```


```{r}
bacteria_sampled_table %>% 
  dplyr::group_by(organism_name) %>% 
  dplyr::slice(1) %>% 
  dplyr::ungroup() %>% 
  dplyr::summarise(
    needed_samples = sum(num_samples),
    actual_samples = sum(sampled_number)
  )
```

Then we check if there are any duplicate sequences within the samples.

```{r}
bacteria_sampled_table %>% blast_with_ifself(
  col_id = ID,
  col_seq = sequence,
  percent_threshold = 90
) %>% 
  knitr::kable()
```

```{r}
bacteria_sampled_table %>% blast_with_ifself(
  col_id = ID,
  col_seq = sequence,
  percent_threshold = 10
) %>% 
  knitr::kable()
```

#### Save results

```{r}
# bacteria_sampled_table %>%
#   saveRDS(here::here("scripts/r-scripts/getting-secreted-data", "bacteria_sampled_table_good02.RDS"))
```



### Run with fungi

#### Load sequence and lookup data

```{r}
# Read the full table of the prediction result of the SignalP
fungi_full_table <- data.table::fread(here::here("data/secreted_data/updated_signalp_results", "fungi_full_table.csv")) %>%
  # Make the name of organisms consistent with the lookup table
  mutate(
    organism_name = organism_name %>%
      stringr::str_replace_all("^_", "") %>%
      stringr::str_to_lower()
  ) %>%
  dplyr::filter(prediction == "Signal peptide", signalp_prob > 0.9)
```

```{r}
fungi_lookup_table <- data.table::fread(here::here("data/secreted_data/signalp-pipeline", "fungi_lookup_table.csv")) %>%
  # `colnames<-`(c("Pathogenspecies", "Count")) %>%
  group_by(Pathogenspecies) %>%
  summarise(samples_needed = sum(Count)) %>%
  ungroup()

fungi_lookup_table <- fungi_lookup_table %>%
  mutate(
    Pathogenspecies = Pathogenspecies %>%
      stringr::str_to_lower() %>%
      stringr::str_remove_all("\\.") %>%
      stringr::str_replace_all(" ", "_")
  )

fungi_lookup_table <- fungi_lookup_table %>%
  # Manual name fixes
  mutate(
    Pathogenspecies = Pathogenspecies %>%
      stringr::str_replace_all("\\(", "") %>%
      stringr::str_replace_all("\\)", "") %>%
      stringr::str_replace_all("-", "_"),
    Pathogenspecies = ifelse(
      Pathogenspecies == "pyrenophora_tritici_repentis",
      "pyrenophora_triticirepentis",
      Pathogenspecies
    ),
  ) %>%
  # Fix repeated Pathogenspecies
  group_by(Pathogenspecies) %>%
  summarise(samples_needed = sum(samples_needed))
```

#### Merge sequence data with lookup

```{r}
fungi_merged_table <- merge_data_with_lookup_table(
  bag_data = fungi_full_table,
  bag_var = organism_name,
  lookup_data = fungi_lookup_table,
  lookup_var = Pathogenspecies
)

# Check if the merged table doesn't have any NAs
if (
  length(
    fungi_merged_table %>%
      filter(samples_needed %>% is.na()) %>%
      pull(organism_name) %>% unique()
  ) == 0
) {
  rm(fungi_full_table, fungi_lookup_table)
}
```

#### Sample sequences

```r
fungi_sampled_table <- fungi_merged_table %>%
  map_sampleing_function(
    col_organism = organism_name, 
    col_id = ID, 
    col_seq = sequence
  )
```

#### Check quality of samples

We check first if enough samples were obtained compares to the needed samples from the lookup table.

```{r}
fungi_sampled_table <- readRDS("../../../data/secreted_data/ready_to_process/sampled_data_without_identical/fungi_sampled_table_good.RDS")
```


```{r}
fungi_sampled_table %>% 
  dplyr::group_by(organism_name) %>% 
  dplyr::slice(1) %>% 
  dplyr::ungroup() %>% 
  dplyr::summarise(
    needed_samples = sum(samples_needed),
    actual_samples = sum(samples_obtained)
  )
```

Then we check if there are any duplicate sequences within the samples.
```{r}
fungi_sampled_table %>% blast_with_ifself(
  col_id = ID,
  col_seq = sequence,
  percent_threshold = 90
) %>% 
  knitr::kable()
```

```{r}
fungi_sampled_table %>% blast_with_ifself(
  col_id = ID,
  col_seq = sequence,
  percent_threshold = 10
) %>% 
  knitr::kable()
```

#### Save results

```{r}
# fungi_sampled_table %>%
  # saveRDS(here::here("scripts/r-scripts/getting-secreted-data", "fungi_sampled_table_good01.RDS"))
```


### Run with oomycete

#### Load sequence and lookup data

```{r}
# Read the full table of the prediction result of the SignalP
oomycete_full_table <- data.table::fread(here::here("data/secreted_data/updated_signalp_results", "protists_full_table.csv")) %>%
  # Make the name of organisms consistent with the lookup table
  mutate(
    organism_name = organism_name %>%
      stringr::str_replace_all("^_", "") %>%
      stringr::str_to_lower()
  ) %>%
  dplyr::filter(prediction == "Signal peptide", signalp_prob > 0.9)
```

```{r}
oomycete_lookup_table <- data.table::fread(here::here("data/secreted_data/signalp-pipeline", "oomycete_lookup_table.csv")) %>%
  # `colnames<-`(c("Pathogenspecies", "Count")) %>%
  group_by(Pathogenspecies) %>%
  summarise(samples_needed = sum(Count)) %>%
  ungroup()

oomycete_lookup_table <- oomycete_lookup_table %>%
  mutate(
    Pathogenspecies = Pathogenspecies %>%
      stringr::str_to_lower() %>%
      stringr::str_remove_all("\\.") %>%
      stringr::str_replace_all(" ", "_")
  )

oomycete_lookup_table <- oomycete_lookup_table %>%
  # Manual name fixes
  mutate(
    Pathogenspecies = Pathogenspecies %>%
      stringr::str_replace_all("\\(", "") %>%
      stringr::str_replace_all("\\)", "") %>%
      stringr::str_replace_all("-", "_")
  ) %>%
  # Fix repeated Pathogenspecies
  group_by(Pathogenspecies) %>%
  summarise(samples_needed = sum(samples_needed))
```

#### Merge sequence data with lookup

```{r}
oomycete_merged_table <- merge_data_with_lookup_table(
  bag_data = oomycete_full_table,
  bag_var = organism_name,
  lookup_data = oomycete_lookup_table,
  lookup_var = Pathogenspecies
)

# Check if the merged table doesn't have any NAs
if (
  length(
    oomycete_merged_table %>%
      filter(samples_needed %>% is.na()) %>%
      pull(organism_name) %>% unique()
  ) == 0
) {
  rm(oomycete_full_table, oomycete_lookup_table)
}
```

#### Sample sequences

```r
oomycete_sampled_table <- oomycete_merged_table %>%
  map_sampleing_function(
    col_organism = organism_name, 
    col_id = ID, 
    col_seq = sequence
  )
```

#### Check quality of samples

We check first if enough samples were obtained compares to the needed samples from the lookup table.

```{r}
oomycete_sampled_table <- readRDS("../../../scripts/r-scripts/getting-secreted-data/oomycete_sampled_table_good.RDS")
```


```{r}
oomycete_sampled_table %>% 
  dplyr::group_by(organism_name) %>% 
  dplyr::slice(1) %>% 
  dplyr::ungroup() %>% 
  dplyr::summarise(
    needed_samples = sum(samples_needed),
    actual_samples = sum(samples_obtained)
  )
```

Then we check if there are any duplicate sequences within the samples.
```{r}
oomycete_sampled_table %>% blast_with_ifself(
  col_id = ID,
  col_seq = sequence,
  percent_threshold = 90
) %>% 
  knitr::kable()
```

```{r}
oomycete_sampled_table %>% blast_with_ifself(
  col_id = ID,
  col_seq = sequence,
  percent_threshold = 10
) %>% 
  knitr::kable()
```

#### Save results

```{r}
# oomycete_sampled_table %>%
#   saveRDS(here::here("scripts/r-scripts/getting-secreted-data", "oomycete_sampled_table_good01.RDS"))
```

