---
title: "Untitled"
author: "Ruth Kristianingsih"
date: "19/01/2020"
knit: (function(inputFile, encoding) { rmarkdown::render(inputFile, encoding = encoding, output_dir = here::here("reports", stringr::str_remove(getwd(), here::here("scripts/r-scripts/")))) })
output:
  md_document:
    variant: markdown_github
---

# Selecting the secreted data randomly from the SignalP-Prediction results

In this report, a process to get the secreted data randomly will be shown. First, 

## Function

```{r setup}
library(tidyverse)
```

```{r}
merge_data_withlookup_table <- function(data, data_var, lookup, lookup_var) {
  # Create lookup pattern for base_name
  lookup_pattern <- lookup %>%
    # Arrange by level of "specificity"
    select(patterns = {{ lookup_var }}) %>%
    mutate(
      specificity_level = stringr::str_count(patterns, "_")
    ) %>%
    arrange(desc(specificity_level)) %>%
    # Get vector
    pull(patterns) %>%
    as.character() %>%
    # Create regex pattern
    paste0("^", ., collapse = "|")

  merged_table <- dplyr::left_join(
    # Data with new base_names column
    data %>%
      dplyr::rowwise() %>%
      dplyr::mutate(
        base_names =
          stringr::str_match(
            string = {{ data_var }},
            pattern = lookup_pattern
          ) %>%
            .[1] %>%
            as.character()
      ),
    # Lookup table with base_names
    lookup %>%
      dplyr::mutate_at(
        .vars = dplyr::vars({{ lookup_var }}),
        .funs = as.character
      ) %>%
      dplyr::select(base_names = {{ lookup_var }}, total_count),
    by = "base_names"
  ) %>%
    # Take samples
    dplyr::filter(!is.na(base_names)) %>%
    dplyr::group_by(base_names) %>%
    dplyr::mutate(
      available_count = n(),
      enough_raw_data = available_count >= total_count
    ) %>%
    dplyr::select(-available_count)

  # Take samples without replacement for available data
  # data_with_enough <- merged_table %>%
  #   dplyr::filter(enough_data) %>%
  #   dplyr::group_by(base_names) %>%
  #   dplyr::sample_n(
  #     size = total_count,
  #     replace = FALSE
  #   )

  # Take samples with replacement when missing data
  # data_without_enough <- merged_table %>%
  #   dplyr::filter(!enough_data) %>%
  #   dplyr::group_by(base_names) %>%
  #   dplyr::sample_n(
  #     size = total_count,
  #     replace = TRUE
  #   )
  
  # Merge again
  # merged_table <- rbind(
  #   data_with_enough,
  #   data_without_enough
  # ) %>%
  #   # Remove intermediary base_names column
  #   dplyr::ungroup() %>%
  #   dplyr::mutate(oversampled = !enough_data) %>%
  #   dplyr::select(
  #     # -base_names,
  #     -enough_data
  #   )

  return(merged_table)
}
```


## Bacteria

```{r}
# bacteria_lookup_table <- data.table::fread("../../../data/secreted_data/dataset-download-scripts/pathogen_species_final.csv") %>%
#   `colnames<-`(c("Pathogenspecies", "Count")) %>%
#   group_by(Pathogenspecies) %>%
#   summarise(total_count = sum(Count))
#
# # Read the data file results
# bacteria_full_table <-
#   data.table::fread("../../../data/secreted_data/signalp-pipeline/bacteria_full_table.csv") %>%
#   # Filter only data with signal peptide and with prediction > 0.9
#   dplyr::filter(prediction == "Signal peptide", signalp_prob > 0.9)
```

```{r}
# Read the full table pf the prediction result of the SignalP

bacteria_full_table <- data.table::fread("../../../data/secreted_data/updated_signalp_results/bacteria_full_table.csv") %>%
  # Make the name of organisms consistent with the lookup table
  mutate(
    organism_name = organism_name %>%
      stringr::str_replace_all("^_", "")  %>%
      stringr::str_to_lower()
  ) %>% 
  dplyr::filter(prediction == "Signal peptide", signalp_prob > 0.9)


bacteria_lookup_table <- data.table::fread("../../../data/secreted_data/dataset-download-scripts/pathogen_species_final.csv") %>%
  `colnames<-`(c("Pathogenspecies", "Count")) %>%
  group_by(Pathogenspecies) %>%
  summarise(total_count = sum(Count))

bacteria_lookup_table <- bacteria_lookup_table %>%
  mutate(
    Pathogenspecies = Pathogenspecies %>%
      stringr::str_to_lower() %>%
      stringr::str_remove_all("\\.") %>%
      stringr::str_replace_all(" ", "_")
  )

bacteria_lookup_table <- bacteria_lookup_table %>%
  ungroup() %>% 
  # Manual name fixes
  mutate(
    Pathogenspecies = Pathogenspecies %>%
      stringr::str_replace_all("\\(", "") %>%
      stringr::str_replace_all("\\)", "") %>%
      stringr::str_replace_all("-", "_"),
    Pathogenspecies = ifelse(
      Pathogenspecies == "xanthomonas_citri_subsp_malvacearum",
      "xanthomonas_citri_pv_malvacearum",
      Pathogenspecies
    ),
    Pathogenspecies = ifelse(
      Pathogenspecies == "pantoea_stewartii_subsp_stewartii",
      "pantoea_stewartii",
      Pathogenspecies
    )
  ) %>%
  # Fix repeated Pathogenspecies
  group_by(Pathogenspecies) %>%
  summarise(total_count = sum(total_count))
```


```{r}
bacteria_non_eff_secreted_data  <- sample_from_lookup_table(
  data = bacteria_full_table,
  data_var = organism_name,
  lookup = bacteria_lookup_table,
  lookup_var = Pathogenspecies
)

bacteria_non_eff_secreted_data  %>% 
  saveRDS("../../../data/secreted_data/updated_signalp_results/bacteria_non_eff_secreted_data.RDS")
```

```{r}
bacteria_lookup_table %>%
  knitr::kable()
```


Getting info from the sample data we got 

```{r}
bacteria_sample_data_count <- bacteria_non_eff_secreted_data  %>%
  group_by(organism_name) %>%
  summarise(count = n())

bacteria_sample_data_count
```

### Check the debug on the sampling data

We can check here if there is missing data when we sampling the data randomly. This can due to:

- There is no enough predicted sequence with signalp
- Or this can due to the

```{r}
bacteria_matched_organisms_name <- left_join(
  bacteria_lookup_table %>%
    dplyr::mutate_at(
      .vars = dplyr::vars(Pathogenspecies),
      .funs = as.character
    ) %>%
    dplyr::select(base_names = Pathogenspecies, total_count_src = total_count),
  bacteria_non_eff_secreted_data,
  by = "base_names"
)

# Check if there is NA pathogen organims that can not be mapped
bacteria_matched_organisms_name  %>%
  group_by(base_names) %>%
  slice(1) %>%
  filter(is.na(organism_name)) %>%
  select(base_names, total_count_src, organism_name) %>% 
  knitr::kable()
```

From the results above, as we can see, there is no pathogen organism with missing data. It means that organisms names are mapped. 

## Fungi

```{r}
fungi_lookup_table <- data.table::fread("../../../data/secreted_data/signalp-pipeline/fungi_lookup_table.csv", drop = "V1") %>%
  `colnames<-`(c("Pathogenspecies", "total_count"))

# Lookup table
fungi_lookup_table <- fungi_lookup_table %>%
  mutate(
    Pathogenspecies = Pathogenspecies %>%
      stringr::str_to_lower() %>%
      # stringr::str_remove_all("\\.") %>%
      stringr::str_replace_all(" ", "_"), 
    Pathogenspecies = ifelse(
      Pathogenspecies == "pyrenophora_tritici-repentis",
      "pyrenophora_triticirepentis",
      Pathogenspecies
      )
  )

# Filter for the 
# not_available_fungi <- c("cercospora_apii", "cercospora_beticola", "pyrenophora_tritici-repentis", "melampsora_lini", "parastagonospora_nodorum", "passalora_fulva", "pseudocercospora_fuligena")

# fungi_lookup_table <- fungi_lookup_table %>% 
#   dplyr::filter(!(Pathogenspecies %in% not_available_fungi))

# Read the data file of signalP prediction results
fungi_full_table <-
  data.table::fread("../../../data/secreted_data/updated_signalp_results/fungi_full_table.csv")  %>%
  # Filter only data with signal peptide and with prediction > 0.9
  dplyr::filter(prediction == "Signal peptide", signalp_prob > 0.9)
```




```{r}
# Getting all of the organism name consistent

# Results table
fungi_full_table <- fungi_full_table %>%
  mutate(
    organism_name = organism_name %>%
      stringr::str_replace_all("\\.", "_") %>%
      stringr::str_to_lower()
  )
```


```{r}
fungi_non_eff_secreted_data <- sample_from_lookup_table(
  data = fungi_full_table,
  data_var = organism_name,
  lookup = fungi_lookup_table,
  lookup_var = Pathogenspecies
)

fungi_non_eff_secreted_data %>% 
  saveRDS("../../../data/secreted_data/updated_signalp_results/fungi_non_eff_secreted_data.RDS")
```

### Checking the debug

```{r}
fungi_non_eff_secreted_count <- readRDS("../../../data/secreted_data/updated_signalp_results/fungi_non_eff_secreted_data.RDS") %>% 
  group_by(organism_name) %>% 
  summarise(count = n())

fungi_non_eff_secreted_count %>% 
  dplyr::select(count) %>% 
  sum()

# Compare the lookup table and the result of sampling
data.frame(table = c("result", "lookup"), 
           count_seq = c(fungi_non_eff_secreted_count %>% select(count) %>% 
                           sum(), 
                         fungi_lookup_table %>% select(total_count) %>% 
                           sum()))
```

```{r}
fungi_non_eff_secreted_data <- readRDS("../../../data/secreted_data/updated_signalp_results/fungi_non_eff_secreted_data.RDS")

fungi_debug <- left_join(
  fungi_lookup_table %>%
    dplyr::mutate_at(
      .vars = dplyr::vars(Pathogenspecies),
      .funs = as.character
    ) %>%
    dplyr::select(base_names = Pathogenspecies, total_count_src = total_count),
  fungi_non_eff_secreted_data,
  by = "base_names"
)

fungi_debug %>% 
  group_by(base_names) %>% 
  slice(1) %>% 
  filter(is.na(organism_name)) %>%
  select(base_names, total_count_src, organism_name)

not_available_fungi <- fungi_debug %>% 
  group_by(organism_name, base_names) %>% 
  summarise(count_organism = n()) %>% 
  filter(is.na(organism_name)) 

not_available_fungi_list <- not_available_fungi %>% 
  pull(base_names)

not_available_fungi %>% 
  knitr::kable()
```



## Oomycete


```{r}
oomycete_lookup_table <- data.table::fread("../../../data/secreted_data/signalp-pipeline/oomycete_lookup_table.csv") %>% `colnames<-`(c("Pathogenspecies", "total_count"))


# Read the data file results
oomycete_full_table <-
  data.table::fread("../../../data/secreted_data/updated_signalp_results/protist_full_table.csv") %>%
  # Filter only data with signal peptide and with prediction > 0.9
  dplyr::filter(prediction == "Signal peptide", signalp_prob > 0.9)
```

```{r}
# Getting all of the organism name consistent

# Lookup table
oomycete_lookup_table <- oomycete_lookup_table %>%
  mutate(
    Pathogenspecies = Pathogenspecies %>%
      stringr::str_to_lower() %>%
      # stringr::str_remove_all("\\.") %>%
      stringr::str_replace_all(" ", "_")
  )

# Results table
oomycete_full_table <- oomycete_full_table %>%
  mutate(
    organism_name = organism_name %>%
      stringr::str_replace_all("\\.", "_") %>%
      stringr::str_to_lower()
  )
```

```r
# Only run once
oomycete_non_eff_secreted_data <- sample_from_lookup_table(
  data = oomycete_full_table,
  data_var = organism_name,
  lookup = oomycete_lookup_table,
  lookup_var = Pathogenspecies
)

oomycete_non_eff_secreted_data %>% 
  saveRDS("../../../data/secreted_data/updated_signalp_results/oomycete_non_eff_secreted_data.RDS")
```


```{r}
oomycete_non_eff_secreted_data <- readRDS("../../../data/secreted_data/updated_signalp_results/oomycete_non_eff_secreted_data.RDS")
oomycete_debug <- left_join(
  oomycete_lookup_table %>%
    dplyr::mutate_at(
      .vars = dplyr::vars(Pathogenspecies),
      .funs = as.character
    ) %>%
    dplyr::select(base_names = Pathogenspecies, total_count_src = total_count),
  oomycete_non_eff_secreted_data,
  by = "base_names"
)

not_available_oomycete_list <- 
  oomycete_debug %>% 
  group_by(base_names) %>% 
  filter(is.na(organism_name)) %>%
  select(base_names) %>% 
  pull(base_names)
```


## Summary 

## Checking how many sequence data each pathogen has

```{r}
effector_data_info <- readRDS("../../../data/secreted_data/data_processed_after_signalp/effector_data_info.RDS")

effector_data_info %>%
  group_by(class) %>%
  summarise(count_class = n())
```

After getting the info above, now needs to check the sum of total sequence in lookup table, to make sure that the total is consistent.


```{r}
data.frame(
  pathogen = c("bacteria", "fungi", "oomycete"),
  num_seq = c(
    bacteria_lookup_table %>% dplyr::select(total_count) %>% sum(),
    fungi_lookup_table %>% dplyr::select(total_count) %>% sum(),
    oomycete_lookup_table %>% dplyr::select(total_count) %>% sum()
  )
)
```

#### Bacteria

```{r}
num_seq_retrieved <- bacteria_non_eff_secreted_data %>% 
  nrow()

num_seq_needed <- bacteria_lookup_table %>% 
  select(total_count) %>% 
  sum()

# Summary of all the total count of the sequences needed, not available, and successfully needed
data.frame(desc = c("retrieved_seq", "lookup_table_seq"), 
              count = c(num_seq_retrieved, num_seq_needed)) %>% 
  knitr::kable()
```



#### Fungi

List of fungi that does not exist 


```{r}
num_seq_retrieved <- fungi_non_eff_secreted_count %>% 
  select(count) %>% 
  sum()

num_seq_needed <- fungi_lookup_table %>% 
  select(total_count) %>% 
  sum()

num_seq_na <- fungi_lookup_table %>%
  dplyr::filter(Pathogenspecies %in% not_available_fungi_list) %>% 
  select(total_count) %>% 
  sum()

# Summary of all the total count of the sequences needed, not available, and successfully needed
data.frame(desc = c("retrieved_seq", "lookup_table_seq", "na_seq"), 
              count = c(num_seq_retrieved, num_seq_needed, num_seq_na)) %>% 
  knitr::kable()
```


#### Oomycete


```{r}
num_seq_retrieved <- oomycete_non_eff_secreted_data %>% 
  nrow()

num_seq_needed <- oomycete_lookup_table %>% 
  select(total_count) %>% 
  sum()

num_seq_na <- oomycete_lookup_table %>%
  dplyr::filter(Pathogenspecies %in% not_available_oomycete_list) %>% 
  select(total_count) %>% 
  sum()

data.frame(desc = c("retrieved_seq", "lookup_table_seq", "na_seq"), 
           count = c(num_seq_retrieved, num_seq_needed, num_seq_na)) %>% 
  knitr::kable()
```

## Get rid of the effector data where the non-effector data does not exist

```{r}
effector_species_proteinID <- readRDS("../../../data/secreted_data/data_processed_after_signalp/effector_data_info.RDS") %>% 
  dplyr::select(c("Pathogenspecies", "ProteinID"))
```


```{r}
effector_proteinID_seq_class <- readRDS("../../../data/secreted_data/data_processed_after_signalp/eff_seq_with_class.RDS")
```

We then need to left join them

```{r}
effector_complete <- effector_proteinID_seq_class %>% 
  left_join(., effector_species_proteinID, by = "ProteinID") %>% 
  dplyr::filter(class %in% c("fungi", "oomycete", "bacteria")) 

effector_complete <- effector_complete %>%
  dplyr::mutate(Pathogenspecies = stringr::str_to_lower(Pathogenspecies)) %>%
  dplyr::mutate(Pathogenspecies = stringr::str_replace_all(Pathogenspecies, " ", "_"))

effector_complete %>% 
  saveRDS("../../../data/secreted_data/data_processed_after_signalp/effector_complete_three_pathogens.RDS")
```

```r
effector_complete <- readRDS("../../../data/secreted_data/data_processed_after_signalp/effector_complete_three_pathogens.RDS") %>% 
  dplyr::filter(!(Pathogenspecies %in% c(not_available_fungi_list, not_available_oomycete_list)))

effector_complete %>% 
  saveRDS("../../../data/secreted_data/data_processed_after_signalp/effector_final_after_blast.RDS")

```




