---
title: "Untitled"
author: "Ruth Kristianingsih"
date: "03/02/2020"
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding, output_dir = "../../../reports/getting-data-secreted") })
output:
  md_document:
    variant: markdown_github
---

# Split and Encode data after all sampled and having no identical protein

## Background

After having all data sampled and making sure there is no identical protein (more than 90% identical), then the data is ready to be processed (splitted and encoded)

## Functions

### Load libraries

```{r setup, message=FALSE}
library(docstring)
library(tidyverse)
# library(taxize)
library(caret)
# reticulate::use_condaenv(condaenv = "tensorflow2", conda = "/anaconda3/bin/conda")

# Get the source of the function used to split the data
source(here::here("scripts/r-scripts/r-functions", "split_datasets.R"))
```

### Define functions

```{r}
get_seq_each_class <- function(df_effector, class_var) {
  df_seq <- df_effector %>%
    dplyr::filter(class == class_var) %>%
    dplyr::select(Sequence)

  return(df_seq)
}
```

### Load the data

```{r}
effector_final_after_blast <- readRDS("../../../data/secreted_data/data_processed_after_signalp/effector_final_after_blast.RDS")

effector_seq_fungi <- get_seq_each_class(effector_final_after_blast, class_var = "fungi")
effector_seq_bacteria <- get_seq_each_class(effector_final_after_blast, class_var = "bacteria")
effector_seq_oomycete <- get_seq_each_class(effector_final_after_blast, class_var = "oomycete")
```


### Get the non-effector from randomly sampling data

```{r}
non_effector_seq_fungi <- readRDS("../../../data/secreted_data/ready_to_process/sampled_data_without_identical/fungi_sampled_table_good.RDS") %>% 
  dplyr::select(sequence) %>% 
  `colnames<-`("Sequence")
```

```{r}
non_effector_seq_bacteria <- readRDS("../../../data/secreted_data/ready_to_process/sampled_data_without_identical/bacteria_sampled_table_good.RDS")  %>% 
  dplyr::select(sequence) %>% 
  `colnames<-`("Sequence")
```

```{r}
non_effector_seq_oomycete <- readRDS("../../../data/secreted_data/ready_to_process/sampled_data_without_identical/oomycete_sampled_table_good.RDS")  %>% 
  dplyr::select(sequence) %>% 
  `colnames<-`("Sequence")
```


## Splitting data


### For each pathogen organism

### Fungi 

```{r}
# Combine and labeled data
fungi_full_datasets <- get_data_labeled_binary(effector_seq_fungi, non_effector_seq_fungi)

# Splitted data
fungi_splitted <- get_data_splitted(fungi_full_datasets, p1 = 0.6, p2 = 0.2, test_dataset = TRUE)

fungi_splitted[[1]] %>% 
  data.table::fwrite("../../../data/secreted_data/ready_to_process/splitted-data/fungi_training.csv")

fungi_splitted[[2]] %>% 
  data.table::fwrite("../../../data/secreted_data/ready_to_process/splitted-data/fungi_validation.csv")

fungi_splitted[[3]] %>% 
  data.table::fwrite("../../../data/secreted_data/ready_to_process/splitted-data/fungi_testing.csv")
```


### Oomycete 

```{r}
oomycete_full_datasets <- get_data_labeled_binary(effector_seq_oomycete, non_effector_seq_oomycete)

oomycete_splitted <- get_data_splitted(oomycete_full_datasets, p1 = 0.6, p2 = 0.2, test_dataset = TRUE)

oomycete_splitted[[1]] %>% 
  data.table::fwrite("../../../data/secreted_data/ready_to_process/splitted-data/oomycete_training.csv")

oomycete_splitted[[2]] %>% 
  data.table::fwrite("../../../data/secreted_data/ready_to_process/splitted-data/oomycete_validation.csv")

oomycete_splitted[[3]] %>% 
  data.table::fwrite("../../../data/secreted_data/ready_to_process/splitted-data/oomycete_testing.csv")
```


### Bacteria

```{r}
bacteria_full_datasets <- get_data_labeled_binary(effector_seq_bacteria, non_effector_seq_bacteria)

bacteria_splitted <- get_data_splitted(bacteria_full_datasets, p1 = 0.6, p2 = 0.2, test_dataset = TRUE)

bacteria_splitted[[1]] %>% 
  data.table::fwrite("../../../data/secreted_data/ready_to_process/splitted-data/bacteria_training.csv")

bacteria_splitted[[2]] %>% 
  data.table::fwrite("../../../data/secreted_data/ready_to_process/splitted-data/bacteria_validation.csv")

bacteria_splitted[[3]] %>% 
  data.table::fwrite("../../../data/secreted_data/ready_to_process/splitted-data/bacteria_testing.csv")
```

### Data all together

```{r}
# Get both effector and non-effector ready
effector_final <- effector_final_after_blast %>% 
  dplyr::select(Sequence)

non_effector_final <- rbind(non_effector_seq_bacteria, non_effector_seq_fungi, non_effector_seq_oomycete) 

# Combine and label all of the effector and non-effector data 
full_data <- get_data_labeled_binary(effector_final, non_effector_final)

# Split datasets
full_data_splitted <- get_data_splitted(bacteria_full_datasets, p1 = 0.6, p2 = 0.2, test_dataset = TRUE)

full_data_splitted[[1]] %>% 
  data.table::fwrite("../../../data/secreted_data/ready_to_process/splitted-data/all_training.csv")

full_data_splitted[[2]] %>% 
  data.table::fwrite("../../../data/secreted_data/ready_to_process/splitted-data/all_validation.csv")

full_data_splitted[[3]] %>% 
  data.table::fwrite("../../../data/secreted_data/ready_to_process/splitted-data/all_testing.csv")

```



## Encode Data

### For each pathogen data

### Data all together
