---
title: "Untitled"
author: "Ruth Kristianingsih"
date: "28/07/2019"
knit: (function(inputFile, encoding) { rmarkdown::render(inputFile, encoding = encoding, output_dir = here::here("reports", stringr::str_remove(getwd(), here::here("scripts/r-scripts/")))) })
output:
  md_document:
    variant: markdown_github
---

# Hyperparameters scan of fully connected dense network to predict effector protein

## Aim 

### Question

Can the simplest deep learning model (fully connected model) with certain combination of hyperparamaters give us a good accuracy to predict effector and non-effector protein? Which hyperparamater combination will give the best accuracy?

### Purpose

My purpose is to find the hyperparamater combination that can give us best accuracy model. 

## Method

### Procedure

In order to achieve what I aim for, I will conduct a hyperparameter scan using simple fully connected dense network as a base model. I will use RandomizedSearchCV() from Scikit-learn that will scan the combination of hyperparameters randomly. 

## Execution

I sent a job in GPUs, the scripts is available on github.


## Results 

```{r include=FALSE}
library(tidyverse)
```

Load the all of the results of hyperparameter scan and show the best 30 models. 

```{r}
# Read the CSV files
result_hyper_scan <- data.table::fread("../../../../data/model_scripts/result_hyper_tuned_old.csv", drop = 'V1') %>% 
  dplyr::select(params, mean_train_score, mean_test_score)

# Show the best 30 models
result_hyper_scan %>% 
  arrange(desc(mean_test_score)) %>% 
  slice(1:30) %>% 
  knitr::kable() 
```

Then now, print the results of the predicition on the test data using the first 30 models with the best validation accuracy (so called `mean_test_score` on the table above). 

```{r}
# Read the CSV of the prediction results on the test data
predict_results <- data.table::fread("../../../../data/model_scripts/df_result_prediction_old.csv", drop = "V1")

# Show the results by sort the accuracy
predict_results %>% 
  arrange(Accuracy) %>%  
  knitr::kable()
```

## Conclusion

By randomly selecting 100 combination of hyperparameters, and evaluate the first 30 models with the best validation accuracy on the test data, we obtained the best accuracy 77.33 % on the test data. Then, another hypothesis: if we take more than 100 randomly combination of hyperparameters, we may get better accuracy on test data prediction (more than 77.33%). 

## Next Step 

I sent a script on GPU to run a hyperparameter scan by selecting 250 randomly hyperparameter combination and select 100 first models with the best validation accuracy and evaluate on the test data. 
