---
title: "Untitled"
author: "Ruth Kristianingsih"
date: "27/09/2019"
knit: (function(inputFile, encoding) { rmarkdown::render(inputFile, encoding = encoding, output_dir = here::here("reports", stringr::str_remove(getwd(), here::here("scripts/r-scripts/")))) })
output:
  md_document:
    variant: markdown_github
---

# Current Results of Hyperparameters Scanning after the jobs got killed on 20 – 22 September 2019

## Introduction

According to the last results after there was an HPC service discruption, there are severak items need to be done according to Dan's suggestions:

1. Do prediction to the test data for the hyperparamaters space that gave the best accuracy, for the model: 

    - CNN-LSTM
    - CNN-GRU
    
2. Do grid search on the model LSTM

3. Do again RandomizedSearchCV on the model GRU
    

## Execution and Results

### Evaluating on the test data for the model with the combination of hyperparamaters that gives the best accuracy training dan validation data

#### CNN - LSTM with the best parameters

```
Predict using test data using random_search:

  8/150 [>.............................] - ETA: 23s
 16/150 [==>...........................] - ETA: 15s
 24/150 [===>..........................] - ETA: 13s
 32/150 [=====>........................] - ETA: 11s
 40/150 [=======>......................] - ETA: 10s
 48/150 [========>.....................] - ETA: 9s 
 56/150 [==========>...................] - ETA: 8s
 64/150 [===========>..................] - ETA: 7s
 72/150 [=============>................] - ETA: 6s
 80/150 [===============>..............] - ETA: 5s
 88/150 [================>.............] - ETA: 5s
 96/150 [==================>...........] - ETA: 4s
104/150 [===================>..........] - ETA: 3s
112/150 [=====================>........] - ETA: 3s
120/150 [=======================>......] - ETA: 2s
128/150 [========================>.....] - ETA: 1s
136/150 [==========================>...] - ETA: 1s
144/150 [===========================>..] - ETA: 0s
150/150 [==============================] - 12s 81ms/step
acc y_pred_random_search: 0.7133333333333334
```

#### CNN - GRU with the best paramaters


```
Parameters:
	optimizers: Adam
	opt_recurrent_regs: <keras.regularizers.L1L2 object at 0x7f7d0257ed68>
	opt_kernel_regs: <keras.regularizers.L1L2 object at 0x7f7d0257ed68>
	opt_go_backwards: TRUE
	opt_dropout_recurrent: 0
	opt_dropout: 0
	maxpool_size: 3
	kernel_size: 2
	gru_hidden_units: 64
	filter_conv: 48
	epochs: 30
	batch_size: 8
	activation_conv: relu

  8/150 [>.............................] - ETA: 38s
 16/150 [==>...........................] - ETA: 24s
 24/150 [===>..........................] - ETA: 19s
 32/150 [=====>........................] - ETA: 16s
 40/150 [=======>......................] - ETA: 13s
 48/150 [========>.....................] - ETA: 12s
 56/150 [==========>...................] - ETA: 10s
 64/150 [===========>..................] - ETA: 9s 
 72/150 [=============>................] - ETA: 8s
 80/150 [===============>..............] - ETA: 7s
 88/150 [================>.............] - ETA: 6s
 96/150 [==================>...........] - ETA: 5s
104/150 [===================>..........] - ETA: 4s
112/150 [=====================>........] - ETA: 3s
120/150 [=======================>......] - ETA: 3s
128/150 [========================>.....] - ETA: 2s
136/150 [==========================>...] - ETA: 1s
144/150 [===========================>..] - ETA: 0s
150/150 [==============================] - 15s 102ms/step
acc: 0.7133333333333334
```
### CNN - LSTM parallel

According to those results above, using the models with the combination of hyperparameters with the best results did not really give the good or massive improvements on the accuracy (comparing with the best results from fully connected dense layers). Therefore, for these models, a grid search will be done, and the scripts will be divided into 4 to minimize the time for the jobs to run: 

Here are the hyperparamaters and parameters division for each script:

| Script 	| Batch 	| Hidden Unit 	| Filters  	| Filters LSTM    	| Strides 	| Padding 	| Activation Convolution 	| Activation LSTM 	| Optimizers           	| Batch Normalizations 	| Epochs 	|
|--------	|-------	|-------------	|----------	|-----------------	|---------	|---------	|------------------------	|-----------------	|----------------------	|----------------------	|--------	|
| 1      	| 16    	| 16          	| [16, 32] 	| [8, 16, 32, 48] 	| 1       	| Valid   	| None                   	| tanh            	| ['Adam', 'Adadelta'] 	| yes                  	| 30     	|
| 2      	| 16    	| 32          	| [16, 32] 	| [8, 16, 32, 48] 	| 1       	| Valid   	| None                   	| tanh            	| ['Adam', 'Adadelta'] 	| yes                  	| 30     	|
| 3      	| 32    	| 16          	| [16, 32] 	| [8, 16, 32, 48] 	| 1       	| Valid   	| None                   	| tanh            	| ['Adam', 'Adadelta'] 	| yes                  	| 30     	|
| 4      	| 32    	| 32          	| [16, 32] 	| [8, 16, 32, 48] 	| 1       	| Valid   	| None                   	| tanh            	| ['Adam', 'Adadelta'] 	| yes                  	| 30     	|

```{r include=FALSE}
library(tidyverse)
```



```{r include=FALSE}
# Functions ------------------------------------------------

read_log_into_df_with_params_list <- function(file, params_list, numeric_params) {
  # Filter needed info from raw log, store in a vector of strings
  # lines <- system(paste("grep -E 'loss:.*acc:|Epoch'", file), intern = TRUE)
  # lines <- system(paste("grep -E 'loss:.*acc:|Epoch|\\[CV\\]'", file, "| grep -v 'total'"), intern = TRUE)
  lines <- system(paste("cat ", file, " | tr -d '\\000' | grep -E 'loss:.*acc:|Epoch|\\[CV\\]' | grep -v 'total'"), intern = TRUE)

  # Calculate size of vector
  num_lines <- length(lines)
  num_headers <- grep("Epoch", lines) %>% length()
  num_clean_lines <- num_lines - num_headers

  # We initialize the output vector of strings
  clean_lines <- rep(NA, num_clean_lines)
  count <- 1
  run_count <- 0

  # Loop for processing the lines
  params_str <- NULL
  for (i in 1:num_lines) {
    line <- lines[[i]]
    if (stringr::str_detect(line, "\\[CV\\]")) {
      params_str <- line
    } else if (stringr::str_detect(line, "Epoch")) {
      # Store epoch "header"
      epoch_str <- line
      run_count <- run_count + 1
    } else {
      # Store data/log line
      raw_str <- line

      # Paste and save processed lines
      clean_lines[[count]] <- paste(run_count, "-", params_str, "-", epoch_str, "-", raw_str)
      count <- count + 1
    }
  }

  # Transform vector of strings into data frame
  df <- data.frame(as.list(clean_lines)) %>%
    t() %>%
    as_tibble() %>%
    tibble::remove_rownames()

  # Separate single column into desired columns
  df <- df %>%
    tidyr::separate(V1, c("run", "params", "epoch", "step", "eta", "loss", "accuracy"), sep = "-") %>%
    tidyr::separate(params, params_list, sep = ", ") %>%
    dplyr::mutate_at(vars(params_list), function(x) stringr::str_split(x, "=", simplify = TRUE)[, 2]) %>%
    dplyr::mutate_at(
      numeric_params,
      as.numeric
    )

  return(df)
}
```

```{r include=FALSE}
clean_log_df_with_params <- function(data) {

  # Use regex for getting the relevant content of each raw column
  data <- data %>%
    dplyr::mutate(
      epoch = stringr::str_extract(epoch, "[0-9]*/[0-9]*"),
      step = stringr::str_extract(step, "[0-9]*/[0-9]*"),
      loss = stringr::str_extract(loss, "[0-9]*\\.[0-9]*"),
      accuracy = stringr::str_extract(accuracy, "[0-9]*\\.[0-9]*")
    )

  # Change data types and remove useless column
  data <- data %>%
    mutate(
      run = as.numeric(run),
      loss = as.numeric(loss),
      accuracy = as.numeric(accuracy)
    ) %>%
    select(-eta)

  return(data)
}


summarise_log_data_with_params_list <- function(data, params_list) {
  data <- data %>%
    # Get last step of each single run
    group_by_at(vars(c("run", "epoch", params_list))) %>%
    slice(n()) %>%
    # Divide epoch into current and max epoch
    mutate(
      curr_epoch = stringr::str_split(epoch, "/") %>% unlist %>% .[1] %>% as.numeric(),
      max_epoch = stringr::str_split(epoch, "/") %>% unlist %>% .[2] %>% as.numeric(),
    ) %>%
    ungroup() %>%
    # Get final loss/accuracy of each epoch
    dplyr::filter(curr_epoch == max_epoch) %>%
    select(-c(step, epoch, run, curr_epoch)) %>%
    dplyr::rename(epochs = max_epoch) %>%
    mutate(epochs = as.factor(epochs)) %>%
    # Create model variable (5 runs)
    tibble::rowid_to_column(var = "run") %>%
    mutate(
      model = cut(run, breaks = seq(0,1000,5), label = 1:200)
    ) %>%
    select(-run) %>%
    # Summarise results
    group_by_at(vars(c("model", "epochs", params_list))) %>%
    summarise(
      loss_mean = mean(loss),
      loss_sd = sd(loss),
      acc_mean = mean(accuracy),
      acc_sd = sd(accuracy)
    )

  return(data)
}
```

#### Script 1

```{r}
src_file_cnn_lstm_1 <- "../../../../results/results/0001-cnn-lstm-scan-batch16-unit16.log"

src_params_list_cnn_lstm <- c(
  "strides", "padding", "optimizers", "number_hidden_units",
  "filters_LSTM", "filters", "epochs_raw", "bn",
  "batch_size", "activation_convolution", "activation_LSTM"
)
src_numeric_params_cnn_lstm <- c(
  "strides", "number_hidden_units", "filters_LSTM",
  "filters", "epochs_raw", "batch_size"
)
```

```{r}
data_cnn_lstm_1 <- src_file_cnn_lstm_1 %>%
  read_log_into_df_with_params_list(src_params_list_cnn_lstm, src_numeric_params_cnn_lstm) %>%
  clean_log_df_with_params()

new_data_cnn_lstm_1 <- data_cnn_lstm_1 %>%
  tidyr::drop_na() %>%
  summarise_log_data_with_params_list(src_params_list_cnn_lstm)
```

```{r}
new_data_cnn_lstm_1 %>% 
  dplyr::select(-c(loss_sd, acc_sd)) %>% 
  dplyr::rename(mean_train_score = acc_mean) %>% 
  knitr::kable()
```


#### Script 2 

```{r}
src_file_cnn_lstm_2 <- "../../../../results/results/0002-cnn-lstm-scan-batch16-unit32.log"
```

```{r}
data_cnn_lstm_2 <- src_file_cnn_lstm_2 %>%
  read_log_into_df_with_params_list(src_params_list_cnn_lstm, src_numeric_params_cnn_lstm) %>%
  clean_log_df_with_params()

new_data_cnn_lstm_2 <- data_cnn_lstm_2 %>%
  tidyr::drop_na() %>%
  summarise_log_data_with_params_list(src_params_list_cnn_lstm)
```

```{r}
new_data_cnn_lstm_2 %>% 
  dplyr::select(-c(loss_sd, acc_sd)) %>% 
  dplyr::rename(mean_train_score = acc_mean) %>% 
  knitr::kable()
```

#### Script 3

```{r}
src_file_cnn_lstm_3 <- "../../../../results/results/0003-cnn-lstm-scan-batch32-unit16.log"
```

```{r}
data_cnn_lstm_3 <- src_file_cnn_lstm_3 %>%
  read_log_into_df_with_params_list(src_params_list_cnn_lstm, src_numeric_params_cnn_lstm) %>%
  clean_log_df_with_params()

new_data_cnn_lstm_3 <- data_cnn_lstm_3 %>%
  tidyr::drop_na() %>%
  summarise_log_data_with_params_list(src_params_list_cnn_lstm)
```

```{r}
new_data_cnn_lstm_3 %>% 
  dplyr::select(-c(loss_sd, acc_sd)) %>% 
  dplyr::rename(mean_train_score = acc_mean) %>% 
  knitr::kable()
```

#### Script 4 (Finished)

```{r}
results_script4_train_val <- data.table::fread("../../../../results/results/all_scan_results_0004-cnn-lstm-scan-batch32-unit32.csv")

results_script4_train_val %>% 
  select(params, mean_train_score, mean_test_score) %>% 
  knitr::kable()
```


```{r}
results_script4_test <- data.table::fread("../../../../results/results/df_pred_results_0004-cnn-lstm-scan-batch32-unit32.csv",  drop = 'V1')

results_script4_test %>% 
  knitr::kable()
```





### CNN - GRU

| Script 	| Batch 	| GRU Hidden Unit 	| Filters  	| Kernel Size 	| Maxpool Size 	| Dropout 	| Dropout Recurrent 	| Activation Convolution 	| Go Backwards 	| Optimizers 	| Regularizer rates 	| Epochs 	|
|--------	|-------	|-----------------	|----------	|-------------	|--------------	|---------	|-------------------	|------------------------	|--------------	|------------	|-------------------	|--------	|
| 1      	| 8     	| 16              	| [32, 48] 	| 2           	| 3            	| 0       	| 0                 	| ['None', 'relu']       	| True         	| Adam       	| [0.01, 0.001]     	| 30     	|
| 2      	| 16    	| 32              	| [32, 48] 	| 2           	| 3            	| 0       	| 0                 	| ['None', 'relu']       	| True         	| Adam       	| [0.01, 0.001]     	| 30     	|
| 3      	| 8     	| 64              	| [32, 48] 	| 2           	| 3            	| 0       	| 0                 	| ['None', 'relu']       	| True         	| Adam       	| [0.01, 0.001]     	| 30     	|
| 4      	| 16    	| 16              	| [32, 48] 	| 2           	| 3            	| 0       	| 0                 	| ['None', 'relu']       	| True         	| Adam       	| [0.01, 0.001]     	| 30     	|
| 5      	| 8     	| 32              	| [32, 48] 	| 2           	| 3            	| 0       	| 0                 	| ['None', 'relu']       	| True         	| Adam       	| [0.01, 0.001]     	|        	|
| 6      	| 16    	| 64              	| [32, 48] 	| 2           	| 3            	| 0       	| 0                 	| ['None', 'relu']       	| True         	| Adam       	| [0.01, 0.001]     	|        	|

```{r}
src_file_cnn_gru_3 <- "../../../../results/results/0007-cnn-gru-grid-batch8_gru_unit64.log"
src_file_cnn_gru_4 <- "../../../../results/results/0008-cnn-gru-grid-batch16_gru_unit16.log"
src_file_cnn_gru_5 <- "../../../../results/results/0017-cnn-gru-grid-batch8_gru_unit32.log"
src_file_cnn_gru_6 <- "../../../../results/results/0018-cnn-gru-grid-batch16_gru_unit64.log"

src_params_list_cnn_gru <- c(
  "reg_rate", "optimizers", "opt_go_backwards",
  "opt_dropout_recurrent", "opt_dropout", "maxpool_size", "kernel_size",
  "gru_hidden_units", "filter_conv", "epochs_raw", "batch_size", "activation_conv"
)
src_numeric_params_cnn_gru <- c(
  "opt_dropout_recurrent", "opt_dropout", "maxpool_size", "kernel_size",
  "gru_hidden_units", "filter_conv", "epochs_raw", "batch_size"
)
```


#### Script 1 (Pending)

This job is still pending to be run in GPU. 

#### Script 2

```{r}
results_cnn_gru_script6_train_val <- data.table::fread("../../../../results/results/all_scan_results_0006-cnn-gru-grid-batch16_gru_unit32.csv")

results_cnn_gru_script6_train_val %>% 
  select(params, mean_train_score, mean_test_score) %>% 
  knitr::kable()
```

```{r}
results_cnn_gru_script6_test <- data.table::fread("../../../../results/results/df_pred_results_0006-cnn-gru-grid-batch16_gru_unit32.csv",  drop = 'V1')

results_cnn_gru_script6_test %>% 
  knitr::kable()
```

#### Script 3

```{r}
data_cnn_gru_3 <- src_file_cnn_gru_3 %>%
  read_log_into_df_with_params_list(src_params_list_cnn_gru, src_numeric_params_cnn_gru) %>%
  clean_log_df_with_params()

new_data_cnn_gru_3 <- data_cnn_gru_3 %>%
  tidyr::drop_na() %>%
  summarise_log_data_with_params_list(src_params_list_cnn_gru)
```

```{r}
new_data_cnn_gru_3 %>% 
  select(-c(loss_sd, acc_sd)) %>% 
  arrange(desc(acc_mean)) %>% 
  dplyr::rename(mean_train_score = acc_mean) %>% 
  knitr::kable()
```

#### Script 4 

```{r}
data_cnn_gru_4 <- src_file_cnn_gru_4 %>%
  read_log_into_df_with_params_list(src_params_list_cnn_gru, src_numeric_params_cnn_gru) %>%
  clean_log_df_with_params()

new_data_cnn_gru_4 <- data_cnn_gru_4 %>%
  tidyr::drop_na() %>%
  summarise_log_data_with_params_list(src_params_list_cnn_gru)
```

```{r}
new_data_cnn_gru_4 %>% 
  select(-c(loss_sd, acc_sd)) %>% 
  arrange(desc(acc_mean)) %>% 
  dplyr::rename(mean_train_score = acc_mean) %>% 
  knitr::kable()
```

#### Script 5

```{r}
data_cnn_gru_5 <- src_file_cnn_gru_5 %>%
  read_log_into_df_with_params_list(src_params_list_cnn_gru, src_numeric_params_cnn_gru) %>%
  clean_log_df_with_params()

new_data_cnn_gru_5 <- data_cnn_gru_5 %>%
  tidyr::drop_na() %>%
  summarise_log_data_with_params_list(src_params_list_cnn_gru)
```

```{r}
new_data_cnn_gru_5 %>% 
  select(-c(loss_sd, acc_sd)) %>% 
  arrange(desc(acc_mean)) %>% 
  dplyr::rename(mean_train_score = acc_mean) %>% 
  knitr::kable()
```

#### Script 6 

```{r}
data_cnn_gru_6 <- src_file_cnn_gru_6 %>%
  read_log_into_df_with_params_list(src_params_list_cnn_gru, src_numeric_params_cnn_gru) %>%
  clean_log_df_with_params()

new_data_cnn_gru_6 <- data_cnn_gru_6 %>%
  tidyr::drop_na() %>%
  summarise_log_data_with_params_list(src_params_list_cnn_gru)
```

```{r}
new_data_cnn_gru_6 %>% 
  select(-c(loss_sd, acc_sd)) %>% 
  arrange(desc(acc_mean)) %>% 
  dplyr::rename(mean_train_score = acc_mean) %>% 
  knitr::kable()
```






### LSTM 

| Script 	| Batch 	| LSTM Units 	| Output Dim 	| Maxpool Size 	| Dropout   	| Dropout Recurrent 	| Activation Convolution 	| Go Backwards      	| Optimizers 	| Regularizer rates 	| Epochs 	|
|--------	|-------	|------------	|------------	|--------------	|-----------	|-------------------	|------------------------	|-------------------	|------------	|-------------------	|--------	|
| 1      	| 8     	| 16         	| 64         	| 3            	| [0, 0.25] 	| 0                 	| ['None', 'relu']       	| ['True', 'False'] 	| Adam       	| [0.01, 0.001]     	| 30     	|
| 2      	| 16    	| 32         	| 64         	| 3            	| [0, 0.25] 	| 0                 	| ['None', 'relu']       	| ['True', 'False'] 	| Adam       	| [0.01, 0.001]     	| 30     	|
| 3      	| 8     	| 16         	| 64         	| 3            	| [0, 0.25] 	| 0                 	| ['None', 'relu']       	| ['True', 'False'] 	| Adam       	| [0.01, 0.001]     	| 30     	|
| 4      	| 16    	| 32         	| 64         	| 3            	| [0, 0.25] 	| 0                 	| ['None', 'relu']       	| ['True', 'False'] 	| Adam       	| [0.01, 0.001]     	| 30     	|

```{r}
src_file_lstm_1 <- "../../../../results/results/0013-lstm-embedding-grid-batch8_lstm_unit16.log"
src_file_lstm_2 <- "../../../../results/results/0014-lstm-embedding-grid-batch16_lstm_unit16_old.log"
src_file_lstm_3 <- "../../../../results/results/0015-lstm-embedding-grid-batch8_lstm_unit32.log"
src_file_lstm_4 <- "../../../../results/results/0016-lstm-embedding-grid-batch16_lstm_unit32.log"

src_params_list_lstm <- c(
  "reg_rate",
  "outputdim", "optimizers", 
  "opt_go_backwards", "opt_dropout_recurrent", "opt_dropout",
  "lstm_hidden_units", "epochs_raw", "batch_size"
)
src_numeric_params_lstm <- c(
  "outputdim", "opt_dropout_recurrent", "opt_dropout",
  "lstm_hidden_units", "epochs_raw", "batch_size"
)
```

#### Script 1

```{r}
data_lstm_1 <- src_file_lstm_1 %>%
  read_log_into_df_with_params_list(src_params_list_lstm, src_numeric_params_lstm) %>%
  clean_log_df_with_params()

new_data_lstm_1 <- data_lstm_1 %>%
  tidyr::drop_na() %>%
  summarise_log_data_with_params_list(src_params_list_lstm)
```

```{r}
new_data_lstm_1 %>% 
  select(-c(loss_sd, acc_sd)) %>% 
  arrange(desc(acc_mean)) %>% 
  dplyr::rename(mean_train_score = acc_mean) %>% 
  knitr::kable()
```

#### Script 2

```{r}
data_lstm_2 <- src_file_lstm_2 %>%
  read_log_into_df_with_params_list(src_params_list_lstm, src_numeric_params_lstm) %>%
  clean_log_df_with_params()

new_data_lstm_2 <- data_lstm_2 %>%
  tidyr::drop_na() %>%
  summarise_log_data_with_params_list(src_params_list_lstm)
```

```{r}
new_data_lstm_2 %>% 
  select(-c(loss_sd, acc_sd)) %>% 
  arrange(desc(acc_mean)) %>% 
  dplyr::rename(mean_train_score = acc_mean) %>% 
  knitr::kable()
```

#### Script 3

```{r}
data_lstm_3 <- src_file_lstm_3 %>%
  read_log_into_df_with_params_list(src_params_list_lstm, src_numeric_params_lstm) %>%
  clean_log_df_with_params()

new_data_lstm_3 <- data_lstm_3 %>%
  tidyr::drop_na() %>%
  summarise_log_data_with_params_list(src_params_list_lstm)
```

```{r}
new_data_lstm_3 %>% 
  select(-c(loss_sd, acc_sd)) %>% 
  arrange(desc(acc_mean)) %>% 
  dplyr::rename(mean_train_score = acc_mean) %>% 
  knitr::kable()
```

#### Script 4

```{r}
data_lstm_4 <- src_file_lstm_4 %>%
  read_log_into_df_with_params_list(src_params_list_lstm, src_numeric_params_lstm) %>%
  clean_log_df_with_params()

new_data_lstm_4 <- data_lstm_4 %>%
  tidyr::drop_na() %>%
  summarise_log_data_with_params_list(src_params_list_lstm)
```

```{r}
new_data_lstm_4 %>% 
  select(-c(loss_sd, acc_sd)) %>% 
  arrange(desc(acc_mean)) %>% 
  dplyr::rename(mean_train_score = acc_mean) %>% 
  knitr::kable()
```


### GRU (RandomGridSearchCV)


```{r}
src_file_gru <- "../../../../results/results/0010_gru-embedding_scan.log"

src_params_list_gru <- c(
  "reg_rate", "outputdim", "optimizers", 
  "opt_go_backwards", "opt_dropout_recurrent", "opt_dropout", "gru_hidden_units",
  "epochs_raw", "batch_size"
)
src_numeric_params_gru <- c(
  "outputdim", "opt_dropout_recurrent", "opt_dropout",
  "gru_hidden_units", "epochs_raw", "batch_size"
)
```


```{r}
data_gru <- src_file_gru %>%
  read_log_into_df_with_params_list(src_params_list_gru, src_numeric_params_gru) %>%
  clean_log_df_with_params()

new_data_gru <- data_gru %>%
  tidyr::drop_na() %>%
  summarise_log_data_with_params_list(src_params_list_gru)
```

```{r}
new_data_gru %>% 
  select(-c(loss_sd, acc_sd)) %>% 
  arrange(desc(acc_mean)) %>% 
  dplyr::rename(mean_train_score = acc_mean) %>% 
  knitr::kable()
```







