---
title: "Getting Non-effector data"
author: "Ruth Kristianingsih"
date: "02/05/2019"
knit: (function(inputFile, encoding) { rmarkdown::render(inputFile, encoding = encoding, output_dir = here::here("reports", stringr::str_remove(getwd(), here::here("scripts/r-scripts/")))) })
output:
  md_document:
    variant: markdown_github
---

# Getting the Non-effector data

## Getting the data from NCBI

In order to get data from NCBI, we can do the following simple query by specifying the name of organism we want to get. 

```sql
"(Name of Organism)"[Organism]
NOT patent US 
NOT virulence[All Fields] 
NOT effector[All Fields]
NOT elicitor[All Fields]
NOT partial[All Fields] 
NOT multispecies[All Fields] 
AND ("2000"[SLEN] : "2500"[SLEN]) 
NOT "Unknown"[Organism]
NOT hypothetical[All Fields]
NOT uncharacterized[All Fields]
NOT unnamed[All Fields]
NOT putative[All Fields]
```
The tables below depicts the list of the number of sequence data for each organism and the categorization of them. 

### Bacteria data
 Bacteria                  | Number |   | Bacteria                    | Number |
|---------------------------|:------:|---|-----------------------------|--------|
| Acinetobacter baumannii   |    1   |   | Mycobacterium tuberculosis  | 1      |
| Aeromonas hydrophila      |    2   |   | Pantoea stewartii           | 2      |
| Aeromonas salmonicida     |    1   |   | Pseudomonas aeruginosa      | 2      |
| Brucella abortus          |    1   |   | Pseudomonas cichorii        | 1      |
| Burkholderia glumae       |    1   |   | Pseudomonas savastanoi      | 14     |
| Burkholderia pseudomallei |   22   |   | Pseudomonas syringae        | 42     |
| Campylobacter jejuni      |    1   |   | Ralstonia solanacearum      | 46     |
| Citrobacter rodentium     |    1   |   | Salmonella enterica         | 64     |
| Clavibacter michiganensis |    2   |   | Shigella flexneri           | 2      |
| Coxiella burnetii         |    3   |   | Staphylococcus aureus       | 1      |
| Cystobacter fuscus        |    1   |   | Vibrio parahaemolyticus     | 1      |
| Edwardsiella ictaluri     |    8   |   | Xanthomonas axonopodis      | 8      |
| Erwinia amylovora         |    9   |   | Xanthomonas campestris      | 16     |
| Escherichia coli          |    6   |   | Xanthomonas oryzae          | 22     |
| Francisella tularensis    |    1   |   | Xylella fastidiosa          | 3      |
| Helicobacter pylori       |    1   |   | Yersinia enterocolitica     | 1      |
| Legionella pneumophila    |    7   |   | Yersinia pestis             | 1      |
| Listeria monocytogenes    |    2   |   | Yersinia pseudotuberculosis | 3      |

### Fungi data

| Fungus                    | Number |   | Fungus                    | Number |
|---------------------------|:------:|---|---------------------------|--------|
| Beauveria bassiana        |    2   |   | Melampsora lini           | 5      |
| Blumeria graminis         |    2   |   | Parastagonospora nodorum  | 2      |
| Botrytis cinerea          |    2   |   | Passalora fulva           | 7      |
| Cercospora apii           |    1   |   | Penicillium expansum      | 4      |
| Cercospora beticola       |    1   |   | Pseudocercospora fuligena | 1      |
| Colletotrichum orbiculare |    1   |   | Puccinia striiformis      | 1      |
| Dothistroma septosporum   |    1   |   | Rhynchosporium commune    | 3      |
| Fusarium oxysporum        |    9   |   | Verticillium dahliae      | 6      |
| Leptosphaeria maculans    |    6   |   | Ustilago maydis           | 2      |
| Magnaporthe oryzae        |   25   |   | Zymoseptoria tritici      | 2      |

### Oomycetes and others data

| Oomycetes                      | Number |   | Others                   | Number  |
|--------------------------------|:------:|---|--------------------------|---------|
| Hyaloperonospora arabidopsidis |    1   |   | Globodera rostochiensis  | 1       |
| Phytophthora cactorum          |    2   |   | Heterodera glycines      | 1       |
| Phytophthora capsici           |   10   |   | Macrosiphum euphorbiae   | 2       |
| Phytophthora infestans         |   15   |   | Toxoplasma gondii        | 1       |
| Phytophthora parasitica        |   17   |   |                          |         |
| Phytophthora sojae             |   23   |   |                          |         |
| Pythium aphanidermatum         |    5   |   |                          |         |
| Plasmopara halstedii           |   10   |   |                          |         |
| Phytophthora megakarya         |   11   |   |                          |         |

Note here that the category others is used for the organism which are neither bacteria, fungi, nor oomycetes. 

## Function to get the unique data and to create dataframe from fasta data

```{r include=FALSE}
library(tidyverse)
```


```r
parse_fasta_data_ncbi <- function(file_path) {
  # Read FASTA file
  fasta_data <- seqinr::read.fasta(file_path)
  # Number of entries
  num_data <- fasta_data %>% length()


  # Create empty data frame
  parsed_data <- data.frame(
    protein_id = rep(NA, num_data),
    protein_fun = rep(NA, num_data),
    pathogen = rep(NA, num_data),
    sequence = rep(NA, num_data)
  )

  for (i in 1:num_data) {
    # Read 'Annot' attribute and parse the string between 'OS=' and 'OX='
    pathogen <- fasta_data[[i]] %>%
      attr("Annot") %>%
      sub(".*\\[ *(.*?) *\\].*", "\\1", .)

    protein_id <- fasta_data[[i]] %>%
      attr("name")

    protein_fun <- fasta_data[[i]] %>%
      attr("Annot") %>%
      stringr::str_remove(protein_id) %>%
      sub(".*> *(.*?) *\\[.*", "\\1", .)

    # Concatenate the vector of the sequence into a single string
    sequence <- fasta_data[[i]] %>%
      as.character() %>%
      toupper() %>%
      paste(collapse = "")

    # Input values into data frame
    parsed_data[i,] <- cbind(protein_id, protein_fun, pathogen, sequence)
  }

  return(parsed_data)
}
```

```r
get_different_sequence_samples <- function(data, samples, seq_chars = 10) {
  data <- data %>%
    mutate(short_sequence = stringr::str_sub(sequence, 1, seq_chars)) %>%
    group_by(short_sequence) %>%
    slice(1) %>%
    ungroup() %>%
    select(-short_sequence) %>% 
    slice(1:samples)
  
  return(data)
}
```


```r
# Run function ---------------------------------------------

# Paths
ncbi_others_path <- "../../../data/getting-data-old/ncbi-others.fasta"
ncbi_fungus_path <- "../../../data/getting-data-old/ncbi-fungus.fasta"
ncbi_oomycetes_path <- "../../../data/getting-data-old/ncbi-oomycetes.fasta"
ncbi_bacteria_path <- "../../../data/getting-data-old/ncbi-bacteria.fasta"
ncbi_bacteria_salmonella_path <- "../../../data/getting-data-old/ncbi-bacteria-salmonella.fasta"
ncbi_bacteria_xanthomonas_path <- "../../../data/getting-data-old/ncbi-bacteria-xanthomonas.fasta"

# Parsed data
ncbi_others_parsed <- parse_fasta_data_ncbi(ncbi_others_path)
ncbi_fungus_parsed <- parse_fasta_data_ncbi(ncbi_fungus_path)
ncbi_oomycetes_parsed <- parse_fasta_data_ncbi(ncbi_oomycetes_path)
ncbi_bacteria_parsed <- parse_fasta_data_ncbi(ncbi_bacteria_path)
ncbi_bacteria_xanthomonas_parsed <- parse_fasta_data_ncbi(ncbi_bacteria_xanthomonas_path)
ncbi_bacteria_salmonella_parsed <- parse_fasta_data_ncbi(ncbi_bacteria_salmonella_path)

# get the data from Salmonella and Xanthomonas
unique_bacteria_xanthomonas_parsed <- get_different_sequence_samples(ncbi_bacteria_xanthomonas_parsed, 22)
unique_bacteria_salmonella_parsed <- get_different_sequence_samples(ncbi_bacteria_salmonella_parsed, 64)

# merge all of data by rows
ncbi_noneffector_parsed <- ncbi_bacteria_parsed %>% 
  rbind(., unique_bacteria_xanthomonas_parsed) %>% 
  rbind(., unique_bacteria_salmonella_parsed) %>% 
  rbind(., ncbi_fungus_parsed) %>% 
  rbind(., ncbi_oomycetes_parsed) %>% 
  rbind(., ncbi_others_parsed)

# Save data frames into CSV files
write.csv(ncbi_noneffector_parsed, "../../../data/getting-data-old/ncbi_noneffector_parsed.csv", row.names = FALSE)
```

```r
# add label on the data frame 
noneffector <- ncbi_noneffector_parsed %>% 
  select(sequence) %>% 
  mutate(label = as.factor(0))

write.csv(noneffector, "../../../data/getting-data-old/noneffector.csv", row.names = FALSE)
```
Now, we can get the data of non-effector with the information of the IDs and also the organism

```{r}
library(tidyverse)
noneffector <- data.table::fread("../../../data/getting-data-old/ncbi_noneffector_parsed.csv") 

noneffector_with_IDs_organism <- noneffector %>% 
  mutate(pathogen_short = word(pathogen, 1, 2, sep = " ")) %>% 
  select(sequence, pathogen_short, protein_id)

# write.csv(noneffector_with_IDs_organism, "../../../data/getting-data-old/noneffector_with_IDs_organism.csv", row.names = FALSE)
```


## View the effector and noneffector data

Afer all of the process done previously, finally we have the noneffector data, and we can view both effector and noneffector data as follows. 

```{r}
effector <- data.table::fread("../../../data/getting-data-old/effector.csv", header = TRUE)
noneffector <- data.table::fread("../../../data/getting-data-old/noneffector.csv", header = TRUE)
```

```{r}
# view the first ten data of effector
effector %>% 
  head(10) %>%
  mutate(sequence = substr(sequence, 1, 30)) %>%
  knitr::kable()
```

```{r}
# view the first ten data of non-effector
noneffector %>% 
  head(10) %>%
  mutate(sequence = substr(sequence, 1, 30)) %>%
  knitr::kable()
```


## Splitting the data into training, development, and testing data sets

In order to splitting data sets, there are several steps need to be done:

1. Combine the effector and noneffector data
2. Using scikit learn package to split the data

```{r}
library(tidyverse)
all_data <- effector %>% 
  rbind(., noneffector)

all_data %>% 
  head(10) %>% 
  knitr::kable()
```

```{r}
# splitting the sequence and label in different dataframe
all_sequence <- all_data %>%
  select(sequence)

all_label <- all_data %>% 
  select(label)
```

```{r}
library(reticulate)
reticulate::use_condaenv("tensorflow", conda = "/anaconda3/bin/conda")
```

```{python}
import pandas as pd
# import numpy as np
```

```{python}
import os
cwd = os.getcwd()
print(cwd)
```

```{r}
py_all_sequence <- r_to_py(all_sequence)
```

```{python}
r.all_sequence
```


